---
title: "Analysis using 3 datasets"
output:
  html_document:
    toc: true
    toc_depth: 4
    theme: united
  word_document:
    toc: true
    toc_depth: '4'
  pdf_document: 
    toc: true
    toc_depth: 4
date: "`r Sys.Date()`"
editor_options:
  markdown:
    wrap: 72
---

# [Does Imipenem-cilastatin less develop/worsen AKI than other carbapenems?]{.underline}

**\_\_**

-   Patients in MIMIC3, MIMIC4, AUMC

-   Those treated with imipenem/cilastatin (I/C group) vs non-cilastatin
    carbapenems (NCC group)

-   Primary outcome is development or progression of AKI (compare AKI
    stage at treatment start and after treatment start)

-   Using propensity score overlap weighting to adjust patients
    backgrounds.

-   Using random mixed effect meta-analysis to combine the results of
    each dataset.

\_\_

## Results (background and outcomes)

\_

### [**1. Backgrounds and outcome development of the patients (before matching)**]{.underline}

Patient characteristics and outcome development in 7 days.

["O, " are the outcomes.]{.underline} **Primary outcome is ["AKI
development or progression"]{.underline}**

```{r table one, fig.height=3, fig.width=6, message=FALSE, warning=FALSE}
library(cobalt) #install.packages("cobalt")
library(pROC)
library(MatchIt) #install.packages("MatchIt")
library(tidyverse)
SELECTS <- c("dataset", "age_cat", "age_group", "sex", "bmi","drug_type", "Imipenem.Cilastatin", "Imipenem.Cilastatin.Relebactam", "time_switch_group", "dep_type",  "time_ICUadmit_to_abx", "pre_blood_culture", "treat_van","vasopressor", "ventilation", "sofa","qsofa", "sirs", "sep3", "base_crea", "near_crea","base_KDIGO", "obs_period", "base_KDIGO_dial", "base_KDIGO_dial", "outcome_KDIGO", "outcome_new_dial", "outcome_KDIGO_inc", "death_in_7d", "outcome_KDIGO_inc_or_death",  "outcome_max_crea_ratio", "outcome_max_crea_diff", "death_in_hosp", "drug") #"ph_htn", "ph_dm", "ph_chf", "ph_ckd", "Meropenem", "Doripenem", "Ertapenem", "los_icu", 

comb_DF <- rbind(
  read.csv("MDF_mimic3.csv") %>% mutate(dataset="MIMIC3", cardiac_surgery=T) %>% dplyr::select(SELECTS, hadm_id) %>% rename("ID"=hadm_id), 
  read.csv("MDF_aumc.csv") %>% mutate(dataset="AUMC", ph_htn=NA, ph_dm=NA, ph_chf=NA, ph_ckd=NA) %>% dplyr::select(SELECTS, icustay_id) %>% rename("ID"=icustay_id) 
  ) %>% 
  rbind(
  read.csv("MDF_miiv.csv") %>% mutate(dataset="miiv") %>% dplyr::select(SELECTS, hadm_id) %>% rename("ID"=hadm_id)
  ) 

comb_DF$base_KDIGO_dial <- ifelse(is.na(comb_DF$base_KDIGO_dial), F, 
                                  ifelse(comb_DF$base_KDIGO_dial>0.5, T, F))
comb_DF$dep_type2 <- ifelse(is.na(comb_DF$dep_type), "Non-surgery", ifelse(comb_DF$dep_type=="surg", "Surgery", "Non-surgery"))
comb_DF$drug_type <- ifelse(comb_DF$drug_type=="IMI", "I/C", "NCC")
comb_DF$sep3 <- ifelse(is.na(comb_DF$sep3), F, ifelse(comb_DF$sep3==T, T, F))
comb_DF$drug01 <- ifelse(comb_DF$drug_type=="I/C", 1 , 0) #convert to 0/1 for matching
comb_DF$drug10 <- ifelse(comb_DF$drug_type=="I/C", 0 , 1)
comb_DF$drug_switch <- ifelse(comb_DF$time_switch_group<168, T, F)
comb_DF$outcome_HDD_in7d <- ifelse(comb_DF$outcome_new_dial==T, T,
                                   ifelse(comb_DF$death_in_7d==T, T, F))
comb_DF$drug_name <- ifelse(grepl("relebactam", comb_DF$drug), "Imipenem/cilastatin/relebactam", 
                      ifelse(grepl("rtapenem", comb_DF$drug), "Ertapenem",
                       ifelse(grepl("Doripenem", comb_DF$drug), "Doripenem",
                        ifelse(grepl("mipenem", comb_DF$drug), "Imipenem/cilastatin",
                         ifelse(grepl("eropenem", comb_DF$drug), "Meropenem", F))))) %>% factor(levels = c("Imipenem/cilastatin", "Imipenem/cilastatin/relebactam","Meropenem", "Doripenem", "Ertapenem"))

library(gtsummary) #install.packages("tableone")
VARS <-c("dataset","age_group", "sex", "bmi",  "dep_type2", "drug_name","sofa", "qsofa", "sirs",  "pre_blood_culture", "treat_van","vasopressor", "ventilation","base_crea", "near_crea","base_KDIGO", "obs_period", "drug_switch","base_KDIGO_dial", "outcome_KDIGO_inc", "death_in_7d", "outcome_KDIGO_inc_or_death", "outcome_new_dial", "outcome_HDD_in7d") #"ph_htn", "ph_dm", "ph_chf", "ph_ckd", "sep3","los_icu", "death_in_hosp", "outcome_max_crea_ratio", "outcome_max_crea_diff"

```

```{r table one 2, warning=F, message=F}
###Ppatietns with base_KDIGO 3 excluded.
comb_DF2 <- comb_DF %>% filter(base_KDIGO<2.9)
CONTIN <- c("qsofa", "sirs", "obs_period")
l_list <- list(dep_type2~"ICU type", treat_van~"pre vancomycin use", vasopressor~"pre vasopressor use", ventilation~"pre ventilation", base_crea~"Baseline sCr", near_crea~"sCr at treatment start", base_KDIGO~"AKI stage at treatment start", obs_period~"observation time", drug_switch~"Cencsored with drug change", base_KDIGO_dial~"RRT at treatment start", outcome_KDIGO_inc~"O, AKI develop/progress", death_in_7d~"O, Death", outcome_KDIGO_inc_or_death~"O, AKI d/p or death", outcome_new_dial~"O, RRT-intervention", outcome_HDD_in7d~"O, Death or RRT-intervention")
#MIMIC3 pts, base_KDIGO<2.9
tbl_summary(comb_DF2 %>% subset(dataset=="MIMIC3"), by=drug_type, include = VARS, type = list(CONTIN ~ "continuous"), digits = list(all_categorical()~ 1, all_continuous() ~ 1), label = l_list) %>% add_p(pvalue_fun = label_style_pvalue(digits = 2)) %>% modify_spanning_header(update = all_stat_cols() ~ "**MIMIC-III, base_KDIGO<3**")

#MIMIC4 pts, base_KDIGO<2.9
tbl_summary(comb_DF2 %>% subset(dataset=="miiv"), by=drug_type, include = VARS, type = list(CONTIN~ "continuous"), digits = list(all_categorical()~ 1, all_continuous() ~ 1), label = l_list) %>% add_p(pvalue_fun = label_style_pvalue(digits = 2)) %>% modify_spanning_header(update = all_stat_cols() ~ "**MIMIC-IV, base_KDIGO<3**")

#AUMC pts, base_KDIGO<2.9
tbl_summary(comb_DF2 %>% subset(dataset=="AUMC"), by=drug_type, include = VARS, type = list(CONTIN ~ "continuous"), digits = list(all_categorical()~ 1, all_continuous() ~ 1), label = l_list) %>% modify_spanning_header(update = all_stat_cols() ~ "**AUMC, base_KDIGO<2.9**") %>% add_p(pvalue_fun = label_style_pvalue(digits = 2))
```

\_\_

### 2. Matching by normal matching (Not used -\> Hidden)

Next, backgrounds are adjusted using (normal) propensity score matching.
Since normal matching cannot adjust the backgrounds enough in some
datasets, [**results with such normal matching were not used for the
manuscript.**]{.underline}

#### 2a. Backgourns and outcome with (normal) propensity score matching (Hidden)

```{r PSM, message=F, warning=F, include=F}
FORMULA <- drug01 ~  age_cat + sex + dep_type2 + sirs + pre_blood_culture+ treat_van + vasopressor + base_crea + near_crea + base_KDIGO #+ dataset
FORMULA0 <- drug01 ~ age_cat + sex + dep_type2 + sirs + pre_blood_culture+ treat_van + vasopressor + base_crea + near_crea + base_KDIGO 

#PSM with MIMIC4
matched_MIMIC4 <- matchit(data=comb_DF2 %>% subset(dataset=="miiv"), FORMULA0, method="nearest", caliper=0.2, distance="glm", link="logit", estimand="ATT", replace=F, ratio=1)
matched_MIMIC4_DF <- matched_MIMIC4 %>% match.data()
tbl_summary(matched_MIMIC4_DF, by=drug_type, include = c(VARS), type = list(CONTIN ~ "continuous"), label = l_list) %>% add_p(pvalue_fun = label_style_pvalue(digits = 2)) %>% modify_spanning_header(update = all_stat_cols() ~ "**PSM, MIMIC-IV")

#PSM with MIMIC3
matched_MIMIC3 <- matchit(data=comb_DF2 %>% subset(dataset=="MIMIC3"), FORMULA0, method="nearest", caliper=0.2, distance="glm", link="logit", estimand="ATT", replace=F, ratio=1)
matched_MIMIC3_DF <- matched_MIMIC3 %>% match.data()
tbl_summary(matched_MIMIC3_DF, by=drug_type, include = c(VARS), type = list(CONTIN ~ "continuous"), label = l_list) %>% add_p(pvalue_fun = label_style_pvalue(digits = 2)) %>% modify_spanning_header(update = all_stat_cols() ~ "**PSM, MIMIC-III**")

#PSM with AUMC
matched_AUMC <- matchit(data=comb_DF2 %>% subset(dataset=="AUMC"), FORMULA0, method="nearest", caliper=0.2, distance="glm", link="logit", estimand="ATT", replace=F, ratio=1)
matched_AUMC_DF <- matched_AUMC %>% match.data()
tbl_summary(matched_AUMC_DF, by=drug_type, include = c(VARS), type = list(CONTIN ~ "continuous"), label = l_list) %>% add_p(pvalue_fun = label_style_pvalue(digits = 2)) %>% modify_spanning_header(update = all_stat_cols() ~ "**PSM, AUMC**")
```

#### 2b. Visualize the quality of matching (Hidden. ROC were around 0.6, SMD were 0.15 at max)

```{r checking PSM, message=F, warning=F, fig.height=4,fig.width=4, include=F}
#Checking the matching quality

#love.plot(matched, threshold=0.1, abs=T, line=T, stars="raw")+ggtitle("PO, all pts")+theme(legend.position="bottom")
love.plot(matched_MIMIC3, threshold=0.1, abs=T, line=T, stars="raw")+ggtitle("PSM-SMD, MIMIC-III")+theme(legend.position="bottom")+xlim(c(0,0.5))
love.plot(matched_MIMIC4, threshold=0.1, abs=T, line=T, stars="raw")+ggtitle("PSM-SMD, MIMIC-IV")+theme(legend.position="bottom")+xlim(c(0,0.5))
love.plot(matched_AUMC, threshold=0.1, abs=T, line=T, stars="raw")+ggtitle("PSM-SMD, AUMC")+theme(legend.position="bottom")+xlim(c(0,0.5))

#roc(matched$treat, matched$distance) %>% auc() %>% round(., digits = 2) %>% paste0("AUC (All data) = ", .)
roc(matched_MIMIC3$treat, matched_MIMIC3$distance) %>% auc() %>% round(., digits = 2) %>% paste0("AUC (MIMIC3) = ", .)
roc(matched_MIMIC4$treat, matched_MIMIC4$distance) %>% auc() %>% round(., digits = 2) %>% paste0("AUC (MIMIC4) = ", .)
roc(matched_AUMC$treat, matched_AUMC$distance) %>% auc() %>% round(., digits = 2) %>% paste0("AUC (AUMC) = ", .)
```

#### 2c. check creatinine change before and after matching (Hidden)

```{r checking crea change, message=F, warning=F}
#creatinine change from 1st-penem (before PSM)
creatinine_c <- readRDS("creatinine_c.rds")
m4_crea4 <- readRDS("m4_crea4.rds")
aumc_crea44 <- read_rds("aumc_crea4.rds") %>% left_join(., read.csv("MDF_aumc.csv") %>% dplyr::select(icustay_id, drug_type) %>% rename("admissionid"=icustay_id), by="admissionid")

c0 <- ggplot(m4_crea4, aes(time_1stabx_to_crea, crea, color=drug_type))+theme_classic()+
  geom_smooth()+xlim(c(-168, 168))+theme(legend.position = "bottom")+coord_cartesian(ylim = c(0.5, 2))+geom_vline(xintercept=0, linetype="dashed")+ggtitle("MIMIC4 w/o PSM")
c1 <- ggplot(creatinine_c, aes(time_abx_to_Crea, creatinine, color=drug_type))+theme_classic()+
  geom_smooth()+xlim(c(-168, 168))+theme(legend.position = "bottom")+coord_cartesian(ylim = c(0.5, 2))+geom_vline(xintercept=0, linetype="dashed")+ggtitle("MIMIC3 w/o PSM")
c2 <- ggplot(aumc_crea44 %>% subset(!is.na(drug_type)), 
       aes(time_abx_to_crea, crea, color=drug_type))+ theme_classic()+
  geom_smooth()+xlim(c(-168, 168))+theme(legend.position = "bottom")+coord_cartesian(ylim = c(0.5, 2))+geom_vline(xintercept=0, linetype="dashed")+ggtitle("AUMC3 w/o PSM")
gridExtra::grid.arrange(c0, c1, c2, nrow=1)


#creatinine change from 1st-penem (after PSM)
c3 <- ggplot(m4_crea4 %>% subset(hadm_id %in% matched_MIMIC4_DF$ID), aes(time_1stabx_to_crea, crea, color=drug_type))+theme_classic()+
  geom_smooth()+xlim(c(-168, 168))+theme(legend.position = "bottom")+coord_cartesian(ylim = c(0.5, 2))+geom_vline(xintercept=0, linetype="dashed")+ggtitle("MIMIC4 w/ PSM")

c4 <- ggplot(creatinine_c %>% subset(hadm_id %in% matched_MIMIC3_DF$ID) %>% rename("crea"=creatinine), aes(time_abx_to_Crea, crea, color=drug_type))+theme_classic()+geom_smooth()+xlim(c(-168, 168))+theme(legend.position = "bottom")+coord_cartesian(ylim = c(0.5, 2))+geom_vline(xintercept=0, linetype="dashed")+ggtitle("MIMIC3 w/ PSM")

c5 <- ggplot(aumc_crea44 %>% subset(admissionid %in% matched_AUMC_DF$ID) %>% subset(!is.na(drug_type)), 
       aes(time_abx_to_crea, crea, color=drug_type))+theme_classic()+
  geom_smooth()+xlim(c(-168, 168))+theme(legend.position = "bottom")+coord_cartesian(ylim = c(0.5, 2))+geom_vline(xintercept=0, linetype="dashed")+ggtitle("AUMC3 w/ PSM")
gridExtra::grid.arrange(c3, c4, c5, nrow=1)
```

####check some eGFR change for notes

```{r checking crea change for supple, message=F, warning=F, fig.width=6, fig.height=5}
library(ggrepel)
for (i in c(14,54)) {
data_n6 <- aumc_crea44 %>% group_by(admissionid) %>% summarise("count"=n()) %>% filter(count>5)
data <- aumc_crea44 %>% subset(admissionid %in% data_n6$admissionid) %>% subset(admissionid %in% matched_AUMC_DF$ID)
data_one_subject <- data %>% subset(admissionid == data$admissionid %>% unique() %>% .[i])
ID <- data_one_subject$admissionid %>% unique()
g<-ggplot(data_one_subject, aes(time_abx_to_crea, crea))+
  theme_classic()+ 
  geom_point()+geom_line()+
  geom_text_repel(aes(label = round(crea, digits=1)))+
  xlim(c(-180, 180))+scale_x_continuous(breaks=c(-168,0,48,168))+
  labs(x="Time from the 1st carbapenem treatment (h)", y="Serum creatinine levels (mg/dL)")+
  theme(legend.position = "none", axis.text.x =  element_text("ccc"))+
  coord_cartesian(ylim = c(0, max(data_one_subject$crea)*1.2))+
    geom_vline(xintercept=0, linetype="dashed", color="gray30")+
    geom_vline(xintercept=-168, linetype="dashed", color="gray80")+
      geom_vline(xintercept=48, linetype="dashed", color="gray80")+
      geom_vline(xintercept=168, linetype="dashed", color="gray80")+
  ggtitle(paste0(i," [ID:",ID, "], KDIGO by crea: ", data_one_subject$base_KDIGO_crea, " -> ", 
                 max(data_one_subject %>% subset(time_abx_to_crea>0) %>% .$outcome_KDIGO_crea, na.rm = T), " (by max), HD_start: ", comb_DF2 %>% subset(ID %in% 3034) %>% .$outcome_new_dial %>% unique()))
  print(g)
  data_n6
}

#data %>% group_by(admissionid) %>% summarise(n())
#data %>% subset(admissionid == data$admissionid %>% unique() %>% .[51])

```

\_\_

### [**3. Overlap weighting**]{.underline}

Propensity score for I/C group was calculated with age, sex, ICU type,
SIRS, pre blood culture, pre vancomycin use, pre vasopressor use,
baseline sCr, sCr at treatment start and AKI stage at treatment start.
Then the overlap weighting was performed on each dataset based on the
propensity scores.

\_\_

#### 3a. backgrounds and outcome development after overlap weighting

```{r ovlp, message=F, warning=F}
#OVERLAP_PSM
library(WeightIt) #install.packages("WeightIt")
library(PSweight) #install.packages("PSweight")
library(survey) #install.packages("survey")
comb_DF2ovl <- comb_DF2 %>% as.data.frame()# %>% subset(data=="MIMIC3")

FORMULA_ovl <- drug01 ~ age_cat + sex  + dep_type2 + sirs + pre_blood_culture+ treat_van + vasopressor + base_crea + near_crea + base_KDIGO 
FORMULA_ovl2 <- drug01 ~  age_cat + sex + dep_type2 + sirs + pre_blood_culture + treat_van + vasopressor + base_crea + near_crea +  base_KDIGO
#dig2s <- c("outcome_max_crea_ratio", "outcome_max_crea_diff","base_crea", "near_crea")

#Create function to do calculating PS, weighing, and showing table.
OVLP<-function(DF0, FORM, TITLE, TITLE2){
DF<-DF0  
bal_ovlp <- PSweight::SumStat(ps.formula = FORM, data = DF, weight="overlap")
ps_man <- glm(formula = FORM, data=DF, family = binomial) %>% .$fitted.values
wgt_man <- DF %>% mutate(ps_for_IMI = ps_man, ovlp_wgt = case_when(drug01 == 1 ~ (1-ps_man), drug01 == 0 ~ ps_man))
saveRDS(bal_ovlp, paste0("bal_ovlp", TITLE, ".rds"))
saveRDS(wgt_man, paste0("wgt_man_", TITLE, ".rds"))

svydesign(~1, data = wgt_man %>% as.data.frame(), weights = wgt_man$ovlp_wgt) %>% tbl_svysummary(include = VARS, by=drug_type, type = list(CONTIN ~ "continuous"), digits = list(all_categorical() ~ 1, all_continuous() ~ 1), label = l_list) %>% 
  add_p(pvalue_fun = label_style_pvalue(digits = 2)) %>%
  modify_header(all_stat_cols() ~ "**{level}** N={style_number(n, scale = 1, digits = 1)}") %>% 
  modify_spanning_header(update = all_stat_cols() ~ TITLE2)
}
```

```{r ovlp results, warning=F, message=F}
#1. overlap-PSM using MIMIC3
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"), FORMULA_ovl2, "Ovlp_MIMIC3", "**Ovlp, MIMIC-III, base_KDIGO<3**")

#2. overlap-PSM using MIMIC4
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"), FORMULA_ovl2, "Ovlp_MIMIC4", "**Ovlp, MIMIC-IV, base_KDIGO<3**")

#3. overlap-PSM using AUMC
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"), FORMULA_ovl2, "Ovlp_AUMC", "**Ovlp, AUMC, base_KDIGO<3**")


#check smd using CreateTableOne package
library(tableone)
library(survey)
library(dplyr)
CreateTableOne(strata = "drug_type", data = readRDS("wgt_man_Ovlp_MIMIC3.rds")) %>% print(smd=T)
```

```{r check smd, include=F}
weighted_design <- svydesign(
  ids = ~1, 
  data = readRDS("wgt_man_Ovlp_AUMC.rds"), 
  weights = ~ovlp_wgt)

weighted_table <- svyCreateTableOne(
  strata = "drug_type", 
  data = weighted_design)
print(weighted_table, smd = TRUE, nonnormal = "age_cat")
```

\_\_

#### 3b. checking matching/weighting quality

```{r ovlp AUC, message=F, warning=F, fig.width=8, fig.height=6}
#Checking ROC
roc(readRDS("wgt_man_Ovlp_MIMIC3.rds")$treat, readRDS("wgt_man_Ovlp_MIMIC3.rds")$ps_for_IMI)%>%auc()%>%round(.,digits = 2)%>%paste0("ovlp_AUC (MIMIC-III) = ", .)
roc(readRDS("wgt_man_Ovlp_MIMIC4.rds")$treat, readRDS("wgt_man_Ovlp_MIMIC4.rds")$ps_for_IMI)%>%auc()%>%round(.,digits = 2)%>%paste0("ovlp_AUC (MIMIC-IV) = ", .)
roc(readRDS("wgt_man_Ovlp_AUMC.rds")$treat, readRDS("wgt_man_Ovlp_AUMC.rds")$ps_for_IMI) %>%auc()%>%round(., digits = 2)%>%paste0("ovlp_AUC (AUMC) = ", .)

#Checking histogram of propensity score
HISTO <- function(DF, TITLE, MARK){
ggplot(DF, aes(ps_for_IMI, group = drug_type, fill=drug_type))+
    geom_histogram(color="black", data = DF %>% subset(drug_type=="I/C"), aes(y=..count..))+
    geom_histogram(color="black", data = DF %>% subset(drug_type!="I/C"), aes(y=-..count..))+
    theme_classic()+
    labs(title =  TITLE, x="Propensity score for I/C group", y="Counts")+
    theme(plot.title = element_text(size = 14, hjust = 0), axis.title.x = element_text(size=10.5))}

tiff("eFigure 1 (histogram).tif", res = 300, width = 8, height = 6, units = "in", compression = "lzw")
gridExtra::grid.arrange(
  HISTO(readRDS("wgt_man_Ovlp_MIMIC3.rds"), "(A) MIMIC-III"), 
  HISTO(readRDS("wgt_man_Ovlp_MIMIC4.rds"), "(B) MIMIC-IV"),
  HISTO(readRDS("wgt_man_Ovlp_AUMC.rds"), "(C) AUMC"), nrow=2)
dev.off()

#Checking SMD
plot(readRDS("bal_ovlpOvlp_MIMIC3.rds"), type="balance", threshold=0.1)
plot(readRDS("bal_ovlpOvlp_MIMIC4.rds"), type="balance")
plot(readRDS("bal_ovlpOvlp_AUMC.rds"), type="balance")
```

\_

#### 3c. Forest plot of the primary outcomes in each dataset and of overall result

\_

```{r ovlp OR, message=F}
#calculating Odds ratio of I/C group in each dataset (not needed)
library(forestplot)
OVLP_OR <- function(DF, FORM, OUTCOME, TITLE){
est_ovlp <- PSweight(ps.formula = FORM, yname = OUTCOME, data = DF, weight = "overlap")
summary1 <- est_ovlp %>% summary(type="OR") %>% .$estimates %>% as.data.frame() %>% 
  mutate(
      OR = exp(Estimate),
      LCI = exp(lwr),
      UCI = exp(upr),
      study = TITLE,
      outcome = OUTCOME
  )
svy_design <- svydesign(~1, data = DF %>% as.data.frame(), weights = DF$ovlp_wgt)
fmla <- as.formula(paste("~", OUTCOME))
summary1 <- summary1 %>% mutate("pts"= svytable(fmla, svy_design) %>% as.data.frame() %>% .$Freq %>% sum(),
                                "events"=svytable(fmla, svy_design) %>% as.data.frame() %>% filter(.data[[OUTCOME]]==T) %>% .$Freq %>% sum())
summary1
}
```

```{r ovlp FP2}
#calculating Odds ratio of I/C group in each dataset
FP2 <- function(RDS, FORM){
OR_RES <- rbind(
  OVLP_OR(readRDS(RDS), FORM, "outcome_KDIGO_inc_or_death", "AKI progression or death"),
  OVLP_OR(readRDS(RDS), FORM, "outcome_KDIGO_inc", "AKI progression"),
  OVLP_OR(readRDS(RDS), FORM, "outcome_new_dial", "Hemodialysis"),
  OVLP_OR(readRDS(RDS), FORM, "death_in_7d", "Death"),
  OVLP_OR(readRDS(RDS), FORM, "outcome_HDD_in7d", "Hemodialysis or death")) %>% 
  mutate("events_percentage"=events/sum(.$event), "pts_percentage"=pts/sum(.$pts))
saveRDS(OR_RES, paste0("ORRES_",RDS))
}

FP2("wgt_man_Ovlp_MIMIC4.rds", FORMULA_ovl2)
FP2("wgt_man_Ovlp_MIMIC3.rds", FORMULA_ovl2)
FP2("wgt_man_Ovlp_AUMC.rds", FORMULA_ovl2)
```

```{r ovlp then RMM, message=F, warning=F}
#Pool the results of each dataset with Random Mixed effect meta-analysis
METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC.rds") %>% mutate("dataset"="AUMC"))
METADF_AKID <- METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
METADF_AKI <- METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
METADF_HD <- METADF0 %>% subset(outcome=="outcome_new_dial")
METADF_D <- METADF0 %>% subset(outcome=="death_in_7d")
METADF_HDD <- METADF0 %>% subset(outcome=="outcome_HDD_in7d")


library(metafor)
METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = METADF_AKID)
METARES_AKI <-rma(yi = Estimate, sei = Std.Error, method = "REML", data = METADF_AKI)
METARES_HD <-rma(yi = Estimate, sei = Std.Error, method = "REML", data = METADF_HD)
METARES_D <-rma(yi = Estimate, sei = Std.Error, method = "REML", data = METADF_D)
METARES_HDD <-rma(yi = Estimate, sei = Std.Error, method = "REML", data = METADF_HDD)

METAF <- function(METARES, AAA, BBB, CCC, TITLE){
metafor::forest(METARES,  atransf=exp, at=log(AAA), slab = dataset,
       xlim=BBB,
       ilab=cbind(round(pts, digits=1), round(events, digits=1)), 
       ilab.lab=c("Subjects","Events"), ilab.pos = 2, ilab.xpos=CCC,
       cex=0.85, header="", xlab="Odds ratio", mlab="Total (Random effects model)", shade=TRUE, 
       main=TITLE, adj=0)
}
SCALEA1<-c(0.25, 1, 4)
SCALEB1 <- c(-5,3)
SCALEC1 <- c(-2.5,-1.5)
#
METAF(METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "AKI development/progression")
METARES_AKI #details of the overall analysis results
METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()

tiff("Figure 2 (primary).tif", res = 300, width = 6, height = 4, units = "in", compression = "lzw")
METAF(METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "AKI development/progression")
dev.off()

METAF(METARES_AKID, SCALEA1, SCALEB1, SCALEC1, "AKI development/progression or death")
tiff("eFigure 3 (sensitivity).tif", res = 300, width = 6, height = 4, units = "in", compression = "lzw")
METAF(METARES_AKID, SCALEA1, SCALEB1, SCALEC1, "AKI development/progression or death")
dev.off()
METARES_AKID
METADF_AKID %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames() 
```

#### 3d. Forest plot of the secondary outcomes

```{r secondaries, message=F, warning=F}
SCALEA2<-c(0.1, 0.5, 1, 2)
SCALEB2 <- c(-8,3)
SCALEC2 <- c(-4.3,-2.8)
METAF(METARES_HD, SCALEA2, SCALEB2, SCALEC2, "(A) RRT-intervention")
METARES_HD
METADF_HD %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()

SCALEA3<-c(0.25, 1, 4)
SCALEB3 <- c(-7,3.5)
SCALEC3 <- c(-3.5,-2)
METAF(METARES_D, SCALEA3, SCALEB3, SCALEC3, "(B) Death")
METARES_D
METADF_D %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()

SCALEA3<-c(0.25, 1, 4)
SCALEB3 <- c(-7,3.5)
SCALEC3 <- c(-3.5,-2)
METAF(METARES_HDD, SCALEA3, SCALEB3, SCALEC3, "(C) RRT-intervention or death")
METARES_HDD
METADF_HDD %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()

#export
tiff("Figure 3 (secondary).tif", 
     width = 5, 
     height = 7,     # Tall file to fit 3 plots vertically
     units = "in", 
     res = 300, 
     compression = "lzw")
par(mfrow = c(3, 1))
METAF(METARES_HD, SCALEA2, SCALEB2, SCALEC2, "(A) RRT-intervention")
METAF(METARES_D, SCALEA3, SCALEB3, SCALEC3, "(B) Death")
METAF(METARES_HDD, SCALEA3, SCALEB3, SCALEC3, "(C) RRT-intervention or death")
dev.off()
```

\_\_

\_\_

### [**4. Stratified analysis**]{.underline}

[**Stratified by AKI stage at treatment start (stage 0 vs stage
1or2)**]{.underline}

Stratify first, then calculate propensity score and perform overlap
weighting.

\_\_

#### 4a. Background and outcome in subgroups before matching.

```{r stratified before PSOW w/o AKI, message=F, warning=F}
###base_KDIGO=0 before PSOW
#MIMIC3
#tbl_summary(comb_DF2 %>% subset(dataset=="MIMIC3"&base_KDIGO==0), by=drug_type, include = c(VARS, outcome_KDIGO_inc), type = list(qsofa ~ "continuous", sirs~ "continuous")) %>% add_p(pvalue_fun = label_style_pvalue(digits = 2)) %>% modify_spanning_header(update = all_stat_cols() ~ "**MIMIC-III, base_KDIGO=0**")
#MIMIC4
#tbl_summary(comb_DF2 %>% subset(dataset=="miiv"&base_KDIGO==0), by=drug_type, include = c(VARS, outcome_KDIGO_inc), type = list(qsofa ~ "continuous", sirs~ "continuous")) %>% add_p(pvalue_fun = label_style_pvalue(digits = 2)) %>% modify_spanning_header(update = all_stat_cols() ~ "**MIMIC-IV, base_KDIGO=0**")
#AUMC
#tbl_summary(comb_DF2 %>% subset(dataset=="AUMC"&base_KDIGO==0), by=drug_type, include = c(VARS, outcome_KDIGO_inc), type = list(qsofa ~ "continuous", sirs~ "continuous")) %>% modify_spanning_header(update = all_stat_cols() ~ "**AUMC, base_KDIGO=0**") %>% add_p(pvalue_fun = label_style_pvalue(digits = 2))
```

\_\_

#### 4b. Background and outcome among those [with AKI at treatment start]{.underline} before matching (Hidden).

```{r stratified before PSOW with AKI, message=F, warning=F}
###base_KDIGO=1or2 before PSOW
#MIMIC3
#tbl_summary(comb_DF2 %>% subset(dataset=="MIMIC3"&base_KDIGO!=0), by=drug_type, include = c(VARS, outcome_KDIGO_inc), type = list(qsofa ~ "continuous", sirs~ "continuous")) %>% add_p(pvalue_fun = label_style_pvalue(digits = 2)) %>% modify_spanning_header(update = all_stat_cols() ~ "**MIMIC-III, base_KDIGO=1,2**")
#MIMIC4
#tbl_summary(comb_DF2 %>% subset(dataset=="miiv"&base_KDIGO!=0), by=drug_type, include = c(VARS, outcome_KDIGO_inc), type = list(qsofa ~ "continuous", sirs~ "continuous")) %>% add_p(pvalue_fun = label_style_pvalue(digits = 2)) %>% modify_spanning_header(update = all_stat_cols() ~ "**MIMIC-IV, base_KDIGO=1,2**")
#AUMC
#tbl_summary(comb_DF2 %>% subset(dataset=="AUMC"&base_KDIGO!=0), by=drug_type, include = c(VARS, outcome_KDIGO_inc), type = list(qsofa ~ "continuous", sirs~ "continuous")) %>% modify_spanning_header(update = all_stat_cols() ~ "**AUMC, base_KDIGO=1,2**") %>% add_p(pvalue_fun = label_style_pvalue(digits = 2))
```

\_\_

#### 4c. Backgrounds, outcomes, matching quality, and forrest plot among those [without AKI]{.underline} [at treatment start.]{.underline}

```{r stratified ovlp base_KDIGO0, message=F, warning=F}
#3. overlap-PSM using MIMIC3, base KDIGO=0
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"&base_KDIGO==0), FORMULA_ovl2, "Ovlp_MIMIC3_base0", "**Ovlp, MIMIC-III, base_KDIGO=0**")
#2. overlap-PSM using MIMIC4, base KDIGO=0
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"&base_KDIGO==0), FORMULA_ovl2, "Ovlp_MIMIC4_base0", "**Ovlp, MIMIC-IV, base_KDIGO=0**")
#3. overlap-PSM using AUMC, base KDIGO=0
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"&base_KDIGO==0), FORMULA_ovl2, "Ovlp_AUMC_base0", paste0("**Ovlp, AUMC", ", base_KDIGO=0**"))

#ROC
roc(readRDS("wgt_man_Ovlp_MIMIC3_base0.rds")$treat, readRDS("wgt_man_Ovlp_MIMIC3_base0.rds")$ps_for_IMI)%>%auc()%>%round(.,digits = 2)%>%paste0("ovlp_AUC base 0 (MIMIC3) = ", .)
roc(readRDS("wgt_man_Ovlp_MIMIC4_base0.rds")$treat, readRDS("wgt_man_Ovlp_MIMIC4_base0.rds")$ps_for_IMI)%>%auc()%>%round(.,digits = 2)%>%paste0("ovlp_AUC base 0 (MIMIC4) = ", .)
roc(readRDS("wgt_man_Ovlp_AUMC_base0.rds")$treat, readRDS("wgt_man_Ovlp_AUMC_base0.rds")$ps_for_IMI) %>%auc()%>%round(., digits = 2)%>%paste0("ovlp_AUC base 0 (AUMC) = ", .)

#histogram
gridExtra::grid.arrange(
HISTO(readRDS("wgt_man_Ovlp_MIMIC3_base0.rds"), "MIMIC-III, base KDIGO=0"),
HISTO(readRDS("wgt_man_Ovlp_MIMIC4_base0.rds"), "MIMIC-IV, base KDIGO=0"),
HISTO(readRDS("wgt_man_Ovlp_AUMC_base0.rds"), "AUMC, base KDIGO=0"), nrow=2)

#Forrestplot
FP2("wgt_man_Ovlp_MIMIC3_base0.rds", FORMULA_ovl2)
FP2("wgt_man_Ovlp_MIMIC4_base0.rds", FORMULA_ovl2)
FP2("wgt_man_Ovlp_AUMC_base0.rds", FORMULA_ovl2)



#
base0_METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_base0.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_base0.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_base0.rds") %>% mutate("dataset"="AUMC"))
base0_METADF_AKID <- base0_METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
base0_METADF_AKI <- base0_METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
base0_METADF_HD <- base0_METADF0 %>% subset(outcome=="outcome_new_dial")
base0_METADF_D <- base0_METADF0 %>% subset(outcome=="death_in_7d")
base0_METADF_HDD <- base0_METADF0 %>% subset(outcome=="outcome_HDD_in7d")
base0_METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = base0_METADF_AKID)
base0_METARES_AKI<-rma(yi = Estimate, sei = Std.Error, method = "REML", data = base0_METADF_AKI)
base0_METARES_HD<-rma(yi = Estimate, sei = Std.Error, method = "REML", data = base0_METADF_HD)
base0_METARES_D<-rma(yi = Estimate, sei = Std.Error, method = "REML", data = base0_METADF_D)
base0_METARES_HDD<-rma(yi = Estimate, sei = Std.Error, method = "REML", data = base0_METADF_HDD)

METAF(base0_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(A) AKI development (without AKI at treatment start)")
base0_METARES_AKI
base0_METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()

METAF(base0_METARES_AKID, SCALEA1, SCALEB1, SCALEC1, "AKI development or death (without AKI at treatment start)")
base0_METARES_AKID
base0_METADF_AKID %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()

METAF(base0_METARES_HD, SCALEA1, SCALEB1, SCALEC1, "(X) RRT-intervention (without AKI at treatment start)")
base0_METARES_HD
base0_METADF_HD %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()

METAF(base0_METARES_D, SCALEA1, SCALEB1, SCALEC1, "(B) Death (without AKI at treatment start)")
base0_METARES_D
base0_METADF_D %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()

METAF(base0_METARES_HDD, SCALEA1, SCALEB1, SCALEC1, "(C) RRT-intervention or death (without AKI at treatment start)")
base0_METARES_HDD
base0_METADF_HDD %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()
```

\_\_

#### 4d. Backgrounds, outcomes, matching quality, and forest plot among those [**with AKI** at treatment start.]{.underline}

```{r stratified ovlp base_KDIGO12, message=F, warning=F}
#1. overlap-PSM using MIMIC3, base KDIGO=0
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"&base_KDIGO>0.1&base_KDIGO<3), FORMULA_ovl2, "Ovlp_MIMIC3_base12", "**Ovlp, MIMIC-III, base_KDIGO 1,2**")
#2. overlap-PSM using MIMIC4, base KDIGO=0
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"&base_KDIGO>0.1&base_KDIGO<3), FORMULA_ovl2, "Ovlp_MIMIC4_base12", "**Ovlp, MIMIC-IV, base_KDIGO 1,2**")
#3. overlap-PSM using AUMC, base KDIGO=0
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"&base_KDIGO>0.1&base_KDIGO<3), FORMULA_ovl2, "Ovlp_AUMC_base12", "**Ovlp, AUMC, base_KDIGO 1,2**")

#ROC
roc(readRDS("wgt_man_Ovlp_MIMIC3_base12.rds")$treat, readRDS("wgt_man_Ovlp_MIMIC3_base12.rds")$ps_for_IMI)%>%auc()%>%round(.,digits = 2)%>%paste0("ovlp_AUC base 1,2 (MIMIC3) = ", .)
roc(readRDS("wgt_man_Ovlp_MIMIC4_base12.rds")$treat, readRDS("wgt_man_Ovlp_MIMIC4_base12.rds")$ps_for_IMI)%>%auc()%>%round(.,digits = 2)%>%paste0("ovlp_AUC base 1,2 (MIMIC4) = ", .)
roc(readRDS("wgt_man_Ovlp_AUMC_base12.rds")$treat, readRDS("wgt_man_Ovlp_AUMC_base12.rds")$ps_for_IMI) %>%auc()%>%round(., digits = 2)%>%paste0("ovlp_AUC base 1,2 (AUMC) = ", .)

#histogram
HISTO(readRDS("wgt_man_Ovlp_MIMIC4_base12.rds"), "MIMIC4, base KDIGO=1,2")
HISTO(readRDS("wgt_man_Ovlp_MIMIC3_base12.rds"), "MIMIC3, base KDIGO=1,2")
HISTO(readRDS("wgt_man_Ovlp_AUMC_base12.rds"), "AUMC, base KDIGO=1,2")

FP2("wgt_man_Ovlp_MIMIC4_base12.rds", FORMULA_ovl2)
FP2("wgt_man_Ovlp_MIMIC3_base12.rds", FORMULA_ovl2)
FP2("wgt_man_Ovlp_AUMC_base12.rds", FORMULA_ovl2)

base12_METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_base12.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_base12.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_base12.rds") %>% mutate("dataset"="AUMC"))
base12_METADF_AKID <- base12_METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
base12_METADF_AKI <- base12_METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
base12_METADF_HD <- base12_METADF0 %>% subset(outcome=="outcome_new_dial")
base12_METADF_D <- base12_METADF0 %>% subset(outcome=="death_in_7d")
base12_METADF_HDD <- base12_METADF0 %>% subset(outcome=="outcome_HDD_in7d")

base12_METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = base12_METADF_AKID)
base12_METARES_AKI <-rma(yi = Estimate, sei = Std.Error, method = "REML", data = base12_METADF_AKI)
base12_METARES_HD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = base12_METADF_HD)
base12_METARES_D <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = base12_METADF_D)
base12_METARES_HDD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = base12_METADF_HDD)

METAF(base12_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(X) AKI progression (with AKI at treatment start)")
base12_METARES_AKI
base12_METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()

METAF(base12_METARES_AKID, SCALEA1, SCALEB1, SCALEC1, "AKI progression or death (with AKI at treatment start)")
base12_METARES_AKID
base12_METADF_AKID %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()

METAF(base12_METARES_HD, SCALEA1, SCALEB1, SCALEC1, "(X) RRT-intervention (with AKI at treatment start)")
base12_METARES_HD
base12_METADF_HD %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()

METAF(base12_METARES_D, SCALEA1, SCALEB1, SCALEC1, "(B) Death (with AKI at treatment start)")
base12_METARES_D
base12_METADF_D %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()

METAF(base12_METARES_HDD, SCALEA1, SCALEB1, SCALEC1, "(C) RRT-intervention or death (with AKI at treatment start)")
base12_METARES_HDD
base12_METADF_HDD %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()
```


\_\_

#### 5c. Backgrounds, outcomes, matching quality, and forrest plot among those [**males**]{.underline} [at treatment start.]{.underline}

```{r stratified ovlp males, message=F, warning=F}

FORMULA_ovl2_sex <- drug01 ~  age_cat + dep_type2 + sirs + pre_blood_culture + treat_van + vasopressor + base_crea + near_crea +  base_KDIGO

#1. overlap-PSM using MIMIC3, "Male"
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"&sex=="Male"), FORMULA_ovl2_sex, "Ovlp_MIMIC3_Male", "**Ovlp, MIMIC-III, Male**")
#2. overlap-PSM using MIMIC4, "Male"
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"&sex=="Male"), FORMULA_ovl2_sex, "Ovlp_MIMIC4_Male", "**Ovlp, MIMIC-IV, Male**")
#3. overlap-PSM using AUMC, "Male"
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"&sex=="Male"), FORMULA_ovl2_sex, "Ovlp_AUMC_Male", paste0("**Ovlp, AUMC", ", Male**"))

#Forrestplot
FP2("wgt_man_Ovlp_MIMIC3_Male.rds", FORMULA_ovl2_sex)
FP2("wgt_man_Ovlp_MIMIC4_Male.rds", FORMULA_ovl2_sex)
FP2("wgt_man_Ovlp_AUMC_Male.rds", FORMULA_ovl2_sex)

Male_METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_Male.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_Male.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_Male.rds") %>% mutate("dataset"="AUMC"))
Male_METADF_AKID <- Male_METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
Male_METADF_AKI <- Male_METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
Male_METADF_HD <- Male_METADF0 %>% subset(outcome=="outcome_new_dial")
Male_METADF_D <- Male_METADF0 %>% subset(outcome=="death_in_7d")
Male_METADF_HDD <- Male_METADF0 %>% subset(outcome=="outcome_HDD_in7d")
Male_METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Male_METADF_AKID)
Male_METARES_AKI<-rma(yi = Estimate, sei = Std.Error, method = "REML", data = Male_METADF_AKI)
Male_METARES_HD<-rma(yi = Estimate, sei = Std.Error, method = "REML", data = Male_METADF_HD)
Male_METARES_D<-rma(yi = Estimate, sei = Std.Error, method = "REML", data = Male_METADF_D)
Male_METARES_HDD<-rma(yi = Estimate, sei = Std.Error, method = "REML", data = Male_METADF_HDD)

METAF(Male_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(A) AKI development/progression (Male)")
Male_METARES_AKI
Male_METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()
```

\_\_

#### 5d. Backgrounds, outcomes, matching quality, and forest plot among those [**Female**]{.underline}

```{r stratified ovlp female, message=F, warning=F}
#1. overlap-PSM using MIMIC3, Female
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"&sex=="Female"), FORMULA_ovl2_sex, "Ovlp_MIMIC3_Female", "**Ovlp, MIMIC-III, Female**")
#2. overlap-PSM using MIMIC4, Female
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"&sex=="Female"), FORMULA_ovl2_sex, "Ovlp_MIMIC4_Female", "**Ovlp, MIMIC-IV, Female**")
#3. overlap-PSM using AUMC, Female
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"&sex=="Female"), FORMULA_ovl2_sex, "Ovlp_AUMC_Female", "**Ovlp, AUMC, Female**")

FP2("wgt_man_Ovlp_MIMIC4_Female.rds", FORMULA_ovl2_sex)
FP2("wgt_man_Ovlp_MIMIC3_Female.rds", FORMULA_ovl2_sex)
FP2("wgt_man_Ovlp_AUMC_Female.rds", FORMULA_ovl2_sex)

Female_METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_Female.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_Female.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_Female.rds") %>% mutate("dataset"="AUMC"))
Female_METADF_AKID <- Female_METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
Female_METADF_AKI <- Female_METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
Female_METADF_HD <- Female_METADF0 %>% subset(outcome=="outcome_new_dial")
Female_METADF_D <- Female_METADF0 %>% subset(outcome=="death_in_7d")
Female_METADF_HDD <- Female_METADF0 %>% subset(outcome=="outcome_HDD_in7d")

Female_METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Female_METADF_AKID)
Female_METARES_AKI <-rma(yi = Estimate, sei = Std.Error, method = "REML", data = Female_METADF_AKI)
Female_METARES_HD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Female_METADF_HD)
Female_METARES_D <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Female_METADF_D)
Female_METARES_HDD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Female_METADF_HDD)

METAF(Female_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(A) AKI development/progression (Female)")
Female_METARES_AKI
Female_METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()
```

\_\_

#### 6c. Backgrounds, outcomes, matching quality, and forrest plot among those [**younger**]{.underline} [at treatment start.]{.underline}

```{r stratified ovlp young, message=F, warning=F}

FORMULA_ovl2_age <- drug01 ~  sex + dep_type2 + sirs + pre_blood_culture + treat_van + vasopressor + base_crea + near_crea +  base_KDIGO
comb_DF2ovl %>%dplyr::select(age_cat, age_group) %>% unique()
#1. overlap-PSM using MIMIC3, "Young"
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"&age_cat<59), FORMULA_ovl2_age, "Ovlp_MIMIC3_Young", "**Ovlp, MIMIC-III, Young**")
#2. overlap-PSM using MIMIC4, "Young"
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"&age_cat<59), FORMULA_ovl2_age, "Ovlp_MIMIC4_Young", "**Ovlp, MIMIC-IV, Young**")
#3. overlap-PSM using AUMC, "Young"
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"&age_cat<59), FORMULA_ovl2_age, "Ovlp_AUMC_Young", paste0("**Ovlp, AUMC, Young**"))

#Forrestplot
FP2("wgt_man_Ovlp_MIMIC3_Young.rds", FORMULA_ovl2_age)
FP2("wgt_man_Ovlp_MIMIC4_Young.rds", FORMULA_ovl2_age)
FP2("wgt_man_Ovlp_AUMC_Young.rds", FORMULA_ovl2_age)

Young_METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_Young.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_Young.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_Young.rds") %>% mutate("dataset"="AUMC"))
Young_METADF_AKID <- Young_METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
Young_METADF_AKI <- Young_METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
Young_METADF_HD <- Young_METADF0 %>% subset(outcome=="outcome_new_dial")
Young_METADF_D <- Young_METADF0 %>% subset(outcome=="death_in_7d")
Young_METADF_HDD <- Young_METADF0 %>% subset(outcome=="outcome_HDD_in7d")
Young_METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Young_METADF_AKID)
Young_METARES_AKI<-rma(yi = Estimate, sei = Std.Error, method = "REML", data = Young_METADF_AKI)
Young_METARES_HD<-rma(yi = Estimate, sei = Std.Error, method = "REML", data = Young_METADF_HD)
Young_METARES_D<-rma(yi = Estimate, sei = Std.Error, method = "REML", data = Young_METADF_D)
Young_METARES_HDD<-rma(yi = Estimate, sei = Std.Error, method = "REML", data = Young_METADF_HDD)

METAF(Young_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(A) AKI development/progression (younger than 60 years)")
Young_METARES_AKI
Young_METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()
```

\_\_

\_\_

#### 6d. Backgrounds, outcomes, matching quality, and forest plot among those [**Older**]{.underline}

```{r stratified ovlp Old, message=F, warning=F}
#1. overlap-PSM using MIMIC3, Older
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"&age_cat>58), FORMULA_ovl2_age, "Ovlp_MIMIC3_Old", "**Ovlp, MIMIC-III, Old**")
#2. overlap-PSM using MIMIC4, Older
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"&age_cat>58), FORMULA_ovl2_age, "Ovlp_MIMIC4_Old", "**Ovlp, MIMIC-IV, Old**")
#3. overlap-PSM using AUMC, Older
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"&age_cat>58), FORMULA_ovl2_age, "Ovlp_AUMC_Old", "**Ovlp, AUMC, Old**")

FP2("wgt_man_Ovlp_MIMIC4_Old.rds", FORMULA_ovl2_age)
FP2("wgt_man_Ovlp_MIMIC3_Old.rds", FORMULA_ovl2_age)
FP2("wgt_man_Ovlp_AUMC_Old.rds", FORMULA_ovl2_age)

Old_METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_Old.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_Old.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_Old.rds") %>% mutate("dataset"="AUMC"))
Old_METADF_AKID <- Old_METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
Old_METADF_AKI <- Old_METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
Old_METADF_HD <- Old_METADF0 %>% subset(outcome=="outcome_new_dial")
Old_METADF_D <- Old_METADF0 %>% subset(outcome=="death_in_7d")
Old_METADF_HDD <- Old_METADF0 %>% subset(outcome=="outcome_HDD_in7d")

Old_METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Old_METADF_AKID)
Old_METARES_AKI <-rma(yi = Estimate, sei = Std.Error, method = "REML", data = Old_METADF_AKI)
Old_METARES_HD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Old_METADF_HD)
Old_METARES_D <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Old_METADF_D)
Old_METARES_HDD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Old_METADF_HDD)

METAF(Old_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(A) AKI development/progression (older than 59 years)")
Old_METARES_AKI
Old_METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()
```


\_\_

#### 7c. Backgrounds, outcomes, matching quality, and forrest plot among those [**vancomycin**]{.underline} [at treatment start.]{.underline}

```{r stratified ovlp vanco, message=F, warning=F}

FORMULA_ovl2_vc <- drug01 ~  age_cat + sex + dep_type2 + sirs + pre_blood_culture + vasopressor + base_crea + near_crea +  base_KDIGO

#1. overlap-PSM using MIMIC3, "Young"
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"&treat_van==T), FORMULA_ovl2_vc, "Ovlp_MIMIC3_vc", "**Ovlp, MIMIC-III, Vancomycin_treated**")
#2. overlap-PSM using MIMIC4, "Young"
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"&treat_van==T), FORMULA_ovl2_vc, "Ovlp_MIMIC4_vc", "**Ovlp, MIMIC-IV, Vancomycin_treated**")
#3. overlap-PSM using AUMC, "Young"
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"&treat_van==T), FORMULA_ovl2_vc, "Ovlp_AUMC_vc", paste0("**Ovlp, AUMC, Vancomycin_treated**"))

#Forrestplot
FP2("wgt_man_Ovlp_MIMIC3_vc.rds", FORMULA_ovl2_vc)
FP2("wgt_man_Ovlp_MIMIC4_vc.rds", FORMULA_ovl2_vc)
FP2("wgt_man_Ovlp_AUMC_vc.rds", FORMULA_ovl2_vc)

vc_METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_vc.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_vc.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_vc.rds") %>% mutate("dataset"="AUMC"))
vc_METADF_AKID <- vc_METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
vc_METADF_AKI <- vc_METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
vc_METADF_HD <- vc_METADF0 %>% subset(outcome=="outcome_new_dial")
vc_METADF_D <- vc_METADF0 %>% subset(outcome=="death_in_7d")
vc_METADF_HDD <- vc_METADF0 %>% subset(outcome=="outcome_HDD_in7d")
vc_METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = vc_METADF_AKID)
vc_METARES_AKI<-rma(yi = Estimate, sei = Std.Error, method = "REML", data = vc_METADF_AKI)
vc_METARES_HD<-rma(yi = Estimate, sei = Std.Error, method = "REML", data = vc_METADF_HD)
vc_METARES_D<-rma(yi = Estimate, sei = Std.Error, method = "REML", data = vc_METADF_D)
vc_METARES_HDD<-rma(yi = Estimate, sei = Std.Error, method = "REML", data = vc_METADF_HDD)

METAF(vc_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(A) AKI development/progression (Treated with vancomycin)")
vc_METARES_AKI
vc_METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()
```

\_\_

\_\_

#### 7d. Backgrounds, outcomes, matching quality, and forest plot among those [**no_vancomycin**]{.underline}

```{r stratified ovlp no vanco, message=F, warning=F}
#1. overlap-PSM using MIMIC3, Older
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"&treat_van==F), FORMULA_ovl2_vc, "Ovlp_MIMIC3_novc", "**Ovlp, MIMIC-III, No_vancomycin**")
#2. overlap-PSM using MIMIC4, Older
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"&treat_van==F), FORMULA_ovl2_vc, "Ovlp_MIMIC4_novc", "**Ovlp, MIMIC-IV, No_vancomycin**")
#3. overlap-PSM using AUMC, Older
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"&treat_van==F), FORMULA_ovl2_vc, "Ovlp_AUMC_novc", "**Ovlp, AUMC, No_vancomycin**")

FP2("wgt_man_Ovlp_MIMIC4_novc.rds", FORMULA_ovl2_vc)
FP2("wgt_man_Ovlp_MIMIC3_novc.rds", FORMULA_ovl2_vc)
FP2("wgt_man_Ovlp_AUMC_novc.rds", FORMULA_ovl2_vc)

novc_METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_novc.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_novc.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_novc.rds") %>% mutate("dataset"="AUMC"))
novc_METADF_AKID <- novc_METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
novc_METADF_AKI <- novc_METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
novc_METADF_HD <- novc_METADF0 %>% subset(outcome=="outcome_new_dial")
novc_METADF_D <- novc_METADF0 %>% subset(outcome=="death_in_7d")
novc_METADF_HDD <- novc_METADF0 %>% subset(outcome=="outcome_HDD_in7d")

novc_METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = novc_METADF_AKID)
novc_METARES_AKI <-rma(yi = Estimate, sei = Std.Error, method = "REML", data = novc_METADF_AKI)
novc_METARES_HD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = novc_METADF_HD)
novc_METARES_D <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = novc_METADF_D)
novc_METARES_HDD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = novc_METADF_HDD)

METAF(novc_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(A) AKI development/progression (No vancomycin)")
novc_METARES_AKI
novc_METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()
```



\_\_

#### 8c. Backgrounds, outcomes, matching quality, and forrest plot among those [**Surgery care unit**]{.underline} [at treatment start.]{.underline}

```{r stratified ovlp surgery, message=F, warning=F}
FORMULA_ovl2_surg <- drug01 ~  age_cat + sex + sirs + pre_blood_culture + treat_van + vasopressor + base_crea + near_crea +  base_KDIGO

#1. overlap-PSM using MIMIC3, "Young"
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"&dep_type2=="Surgery"), FORMULA_ovl2_surg, "Ovlp_MIMIC3_surg", "**Ovlp, MIMIC-III, Surgical unit**")
#2. overlap-PSM using MIMIC4, "Young"
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"&dep_type2=="Surgery"), FORMULA_ovl2_surg, "Ovlp_MIMIC4_surg", "**Ovlp, MIMIC-IV, Surgical unit**")
#3. overlap-PSM using AUMC, "Young"
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"&dep_type2=="Surgery"), FORMULA_ovl2_surg, "Ovlp_AUMC_surg", paste0("**Ovlp, AUMC, Surgical unit**"))

#Forrestplot
FP2("wgt_man_Ovlp_MIMIC3_surg.rds", FORMULA_ovl2_surg)
FP2("wgt_man_Ovlp_MIMIC4_surg.rds", FORMULA_ovl2_surg)
FP2("wgt_man_Ovlp_AUMC_surg.rds", FORMULA_ovl2_surg)

surg_METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_surg.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_surg.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_surg.rds") %>% mutate("dataset"="AUMC"))
surg_METADF_AKID <- surg_METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
surg_METADF_AKI <- surg_METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
surg_METADF_HD <- surg_METADF0 %>% subset(outcome=="outcome_new_dial")
surg_METADF_D <- surg_METADF0 %>% subset(outcome=="death_in_7d")
surg_METADF_HDD <- surg_METADF0 %>% subset(outcome=="outcome_HDD_in7d")
surg_METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = surg_METADF_AKID)
surg_METARES_AKI <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = surg_METADF_AKI)
surg_METARES_HD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = surg_METADF_HD)
surg_METARES_D <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = surg_METADF_D)
surg_METARES_HDD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = surg_METADF_HDD)

METAF(surg_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(A) AKI development/progression (Surgical unit)")
surg_METARES_AKI
surg_METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()
```

\_\_

\_\_

#### 8d. Backgrounds, outcomes, matching quality, and forest plot among those [**non-srugery**]{.underline}

```{r stratified ovlp non-surgery, message=F, warning=F}
#1. overlap-PSM using MIMIC3, Older
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"&dep_type2=="Non-surgery"), FORMULA_ovl2_surg, "Ovlp_MIMIC3_nonsurg", "**Ovlp, MIMIC-III, Non-surgical unit**")
#2. overlap-PSM using MIMIC4, Older
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"&dep_type2=="Non-surgery"), FORMULA_ovl2_surg, "Ovlp_MIMIC4_nonsurg", "**Ovlp, MIMIC-IV, Non-surgical unit**")
#3. overlap-PSM using AUMC, Older
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"&dep_type2=="Non-surgery"), FORMULA_ovl2_surg, "Ovlp_AUMC_nonsurg", "**Ovlp, AUMC, Non-surgical unit**")

FP2("wgt_man_Ovlp_MIMIC4_nonsurg.rds", FORMULA_ovl2_surg)
FP2("wgt_man_Ovlp_MIMIC3_nonsurg.rds", FORMULA_ovl2_surg)
FP2("wgt_man_Ovlp_AUMC_nonsurg.rds", FORMULA_ovl2_surg)

nonsurg_METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_nonsurg.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_nonsurg.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_nonsurg.rds") %>% mutate("dataset"="AUMC"))
nonsurg_METADF_AKID <- nonsurg_METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
nonsurg_METADF_AKI <- nonsurg_METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
nonsurg_METADF_HD <- nonsurg_METADF0 %>% subset(outcome=="outcome_new_dial")
nonsurg_METADF_D <- nonsurg_METADF0 %>% subset(outcome=="death_in_7d")
nonsurg_METADF_HDD <- nonsurg_METADF0 %>% subset(outcome=="outcome_HDD_in7d")

nonsurg_METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = nonsurg_METADF_AKID)
nonsurg_METARES_AKI <-rma(yi = Estimate, sei = Std.Error, method = "REML", data = nonsurg_METADF_AKI)
nonsurg_METARES_HD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = nonsurg_METADF_HD)
nonsurg_METARES_D <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = nonsurg_METADF_D)
nonsurg_METARES_HDD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = nonsurg_METADF_HDD)

METAF(nonsurg_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(A) AKI development/progression (Non-surgical unit)")
nonsurg_METARES_AKI
nonsurg_METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()
```


\_\_

#### 9c. Backgrounds, outcomes, matching quality, and forrest plot among those [**pre bood culture**]{.underline} [at treatment start.]{.underline}

```{r stratified ovlp blood culture, message=F, warning=F}
FORMULA_ovl2_bc <- drug01 ~  age_cat + sex + sirs + dep_type2 + treat_van + vasopressor + base_crea + near_crea +  base_KDIGO
#1. overlap-PSM using MIMIC3, Older
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"&pre_blood_culture==T), FORMULA_ovl2_bc, "Ovlp_MIMIC3_bc", "**Ovlp, MIMIC-III, pre BC**")
#2. overlap-PSM using MIMIC4, Older
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"&pre_blood_culture==T), FORMULA_ovl2_bc, "Ovlp_MIMIC4_bc", "**Ovlp, MIMIC-IV, pre BC**")
#3. overlap-PSM using AUMC, Older
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"&pre_blood_culture==T), FORMULA_ovl2_bc, "Ovlp_AUMC_bc", "**Ovlp, AUMC, pre BC**")

#Forrestplot
FP2("wgt_man_Ovlp_MIMIC3_bc.rds", FORMULA_ovl2_bc)
FP2("wgt_man_Ovlp_MIMIC4_bc.rds", FORMULA_ovl2_bc)
FP2("wgt_man_Ovlp_AUMC_bc.rds", FORMULA_ovl2_bc)

bc_METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_bc.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_bc.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_bc.rds") %>% mutate("dataset"="AUMC"))
bc_METADF_AKID <- bc_METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
bc_METADF_AKI <- bc_METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
bc_METADF_HD <- bc_METADF0 %>% subset(outcome=="outcome_new_dial")
bc_METADF_D <- bc_METADF0 %>% subset(outcome=="death_in_7d")
bc_METADF_HDD <- bc_METADF0 %>% subset(outcome=="outcome_HDD_in7d")
bc_METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = bc_METADF_AKID)
bc_METARES_AKI <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = bc_METADF_AKI)
bc_METARES_HD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = bc_METADF_HD)
bc_METARES_D <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = bc_METADF_D)
bc_METARES_HDD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = bc_METADF_HDD)

METAF(bc_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(A) AKI development/progression (with blood culture)")
bc_METARES_AKI
bc_METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()
```

\_\_

\_\_

#### 9d. Backgrounds, outcomes, matching quality, and forest plot among those [**non-blood culture**]{.underline}

```{r stratified ovlp non-bc, message=F, warning=F}
#1. overlap-PSM using MIMIC3, Older
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"&pre_blood_culture==F), FORMULA_ovl2_bc, "Ovlp_MIMIC3_nonbc", "**Ovlp, MIMIC-III, Non-BC**")
#2. overlap-PSM using MIMIC4, Older
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"&pre_blood_culture==F), FORMULA_ovl2_bc, "Ovlp_MIMIC4_nonbc", "**Ovlp, MIMIC-IV, Non-BC**")
#3. overlap-PSM using AUMC, Older
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"&pre_blood_culture==F), FORMULA_ovl2_bc, "Ovlp_AUMC_nonbc", "**Ovlp, AUMC, Non-BC**")

FP2("wgt_man_Ovlp_MIMIC4_nonbc.rds", FORMULA_ovl2_bc)
FP2("wgt_man_Ovlp_MIMIC3_nonbc.rds", FORMULA_ovl2_bc)
FP2("wgt_man_Ovlp_AUMC_nonbc.rds", FORMULA_ovl2_bc)

nonbc_METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_nonbc.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_nonbc.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_nonbc.rds") %>% mutate("dataset"="AUMC"))
nonbc_METADF_AKID <- nonbc_METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
nonbc_METADF_AKI <- nonbc_METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
nonbc_METADF_HD <- nonbc_METADF0 %>% subset(outcome=="outcome_new_dial")
nonbc_METADF_D <- nonbc_METADF0 %>% subset(outcome=="death_in_7d")
nonbc_METADF_HDD <- nonbc_METADF0 %>% subset(outcome=="outcome_HDD_in7d")

nonbc_METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = nonbc_METADF_AKID)
nonbc_METARES_AKI <-rma(yi = Estimate, sei = Std.Error, method = "REML", data = nonbc_METADF_AKI)
nonbc_METARES_HD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = nonbc_METADF_HD)
nonbc_METARES_D <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = nonbc_METADF_D)
nonbc_METARES_HDD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = nonbc_METADF_HDD)

METAF(nonbc_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(A) AKI development/progression (Non-BC)")
nonbc_METARES_AKI
nonbc_METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()
```



\_\_

#### 10c. Backgrounds, outcomes, matching quality, and forrest plot among those [**SIRS<2**]{.underline} [at treatment start.]{.underline}

```{r stratified ovlp SIRS less than 2, message=F, warning=F}
FORMULA_ovl2_sirs <- drug01 ~ age_cat + sex + dep_type2 + pre_blood_culture + treat_van + vasopressor + base_crea + near_crea +  base_KDIGO

#1. overlap-PSM using MIMIC3, "SIRS<2"
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"&sirs<2), FORMULA_ovl2_sirs, "Ovlp_MIMIC3_Lsirs", "**Ovlp, MIMIC-III, SIRS<2**")
#2. overlap-PSM using MIMIC4, "SIRS<2"
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"&sirs<2), FORMULA_ovl2_sirs, "Ovlp_MIMIC4_Lsirs", "**Ovlp, MIMIC-IV, SIRS<2**")
#3. overlap-PSM using AUMC, "SIRS<2"
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"&sirs<2), FORMULA_ovl2_sirs, "Ovlp_AUMC_Lsirs", paste0("**Ovlp, AUMC, SIRS<2**"))

FP2("wgt_man_Ovlp_MIMIC3_Lsirs.rds", FORMULA_ovl2_sirs)
FP2("wgt_man_Ovlp_MIMIC4_Lsirs.rds", FORMULA_ovl2_sirs)
FP2("wgt_man_Ovlp_AUMC_Lsirs.rds", FORMULA_ovl2_sirs)

Lsirs_METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_Lsirs.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_Lsirs.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_Lsirs.rds") %>% mutate("dataset"="AUMC"))
Lsirs_METADF_AKID <- Lsirs_METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
Lsirs_METADF_AKI <- Lsirs_METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
Lsirs_METADF_HD <- Lsirs_METADF0 %>% subset(outcome=="outcome_new_dial")
Lsirs_METADF_D <- Lsirs_METADF0 %>% subset(outcome=="death_in_7d")
Lsirs_METADF_HDD <- Lsirs_METADF0 %>% subset(outcome=="outcome_HDD_in7d")
Lsirs_METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Lsirs_METADF_AKID)
Lsirs_METARES_AKI <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Lsirs_METADF_AKI)
Lsirs_METARES_HD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Lsirs_METADF_HD)
Lsirs_METARES_D <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Lsirs_METADF_D)
Lsirs_METARES_HDD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Lsirs_METADF_HDD)

METAF(Lsirs_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(A) AKI development/progression (sirs<2)")
Lsirs_METARES_AKI
Lsirs_METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()
```

\_\_

\_\_

#### 10d. Backgrounds, outcomes, matching quality, and forest plot among those [**SIRS>1.99**]{.underline}

```{r stratified ovlp sirs higher than 2, message=F, warning=F}
#1. overlap-PSM using MIMIC3, SIRS>1.99
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"&sirs>1.99), FORMULA_ovl2_sirs, "Ovlp_MIMIC3_Hsirs", "**Ovlp, MIMIC-III, SIRS>1.99**")
#2. overlap-PSM using MIMIC4, SIRS>1.99
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"&sirs>1.99), FORMULA_ovl2_sirs, "Ovlp_MIMIC4_Hsirs", "**Ovlp, MIMIC-IV, SIRS>1.99**")
#3. overlap-PSM using AUMC, SIRS>1.99
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"&sirs>1.99), FORMULA_ovl2_sirs, "Ovlp_AUMC_Hsirs", "**Ovlp, AUMC, SIRS>1.99**")

FP2("wgt_man_Ovlp_MIMIC4_Hsirs.rds", FORMULA_ovl2_sirs)
FP2("wgt_man_Ovlp_MIMIC3_Hsirs.rds", FORMULA_ovl2_sirs)
FP2("wgt_man_Ovlp_AUMC_Hsirs.rds", FORMULA_ovl2_sirs)

Hsirs_METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_Hsirs.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_Hsirs.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_Hsirs.rds") %>% mutate("dataset"="AUMC"))
Hsirs_METADF_AKID <- Hsirs_METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
Hsirs_METADF_AKI <- Hsirs_METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
Hsirs_METADF_HD <- Hsirs_METADF0 %>% subset(outcome=="outcome_new_dial")
Hsirs_METADF_D <- Hsirs_METADF0 %>% subset(outcome=="death_in_7d")
Hsirs_METADF_HDD <- Hsirs_METADF0 %>% subset(outcome=="outcome_HDD_in7d")

Hsirs_METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Hsirs_METADF_AKID)
Hsirs_METARES_AKI <-rma(yi = Estimate, sei = Std.Error, method = "REML", data = Hsirs_METADF_AKI)
Hsirs_METARES_HD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Hsirs_METADF_HD)
Hsirs_METARES_D <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Hsirs_METADF_D)
Hsirs_METARES_HDD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = Hsirs_METADF_HDD)

METAF(Hsirs_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(A) AKI development/progression (SIRS>1.99)")
Hsirs_METARES_AKI
Hsirs_METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()
```

\_\_

#### 11c. Backgrounds, outcomes, matching quality, and forrest plot among those [**with vasopressor**]{.underline} [at treatment start.]{.underline}

```{r stratified ovlp vaso, message=F, warning=F}

FORMULA_ovl2_vaso <- drug01 ~  age_cat + sex + dep_type2 + sirs + pre_blood_culture + treat_van + base_crea + near_crea +  base_KDIGO

#1. overlap-PSM using MIMIC3, vasopressor
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"&vasopressor==T), FORMULA_ovl2_vaso, "Ovlp_MIMIC3_vaso", "**Ovlp, MIMIC-III, with vaso**")
#2. overlap-PSM using MIMIC4, vasopressor
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"&vasopressor==T), FORMULA_ovl2_vaso, "Ovlp_MIMIC4_vaso", "**Ovlp, MIMIC-IV, with vaso**")
#3. overlap-PSM using AUMC, vasopressor
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"&vasopressor==T), FORMULA_ovl2_vaso, "Ovlp_AUMC_vaso", paste0("**Ovlp, AUMC, with vaso**"))

#Forrestplot
FP2("wgt_man_Ovlp_MIMIC3_vaso.rds", FORMULA_ovl2_vaso)
FP2("wgt_man_Ovlp_MIMIC4_vaso.rds", FORMULA_ovl2_vaso)
FP2("wgt_man_Ovlp_AUMC_vaso.rds", FORMULA_ovl2_vaso)

vaso_METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_vaso.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_vaso.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_vaso.rds") %>% mutate("dataset"="AUMC"))
vaso_METADF_AKID <- vaso_METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
vaso_METADF_AKI <- vaso_METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
vaso_METADF_HD <- vaso_METADF0 %>% subset(outcome=="outcome_new_dial")
vaso_METADF_D <- vaso_METADF0 %>% subset(outcome=="death_in_7d")
vaso_METADF_HDD <- vaso_METADF0 %>% subset(outcome=="outcome_HDD_in7d")
vaso_METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = vaso_METADF_AKID)
vaso_METARES_AKI <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = vaso_METADF_AKI)
vaso_METARES_HD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = vaso_METADF_HD)
vaso_METARES_D <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = vaso_METADF_D)
vaso_METARES_HDD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = vaso_METADF_HDD)

METAF(vaso_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(A) AKI development/progression (with vasopressor)")
vaso_METARES_AKI
vaso_METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()
```

\_\_

\_\_

#### 11d. Backgrounds, outcomes, matching quality, and forest plot among those [**non-vasopressor**]{.underline}

```{r stratified ovlp no-vaso, message=F, warning=F}
#1. overlap-PSM using MIMIC3, Older
OVLP(comb_DF2ovl %>% subset(dataset=="MIMIC3"&vasopressor==F), FORMULA_ovl2_vaso, "Ovlp_MIMIC3_nonvaso", "**Ovlp, MIMIC-III, No-vaso**")
#2. overlap-PSM using MIMIC4, Older
OVLP(comb_DF2ovl %>% subset(dataset=="miiv"&vasopressor==F), FORMULA_ovl2_vaso, "Ovlp_MIMIC4_nonvaso", "**Ovlp, MIMIC-IV, No-vaso**")
#3. overlap-PSM using AUMC, Older
OVLP(comb_DF2ovl %>% subset(dataset=="AUMC"&vasopressor==F), FORMULA_ovl2_vaso, "Ovlp_AUMC_nonvaso", "**Ovlp, AUMC, No-vaso**")

FP2("wgt_man_Ovlp_MIMIC4_nonvaso.rds", FORMULA_ovl2_vaso)
FP2("wgt_man_Ovlp_MIMIC3_nonvaso.rds", FORMULA_ovl2_vaso)
FP2("wgt_man_Ovlp_AUMC_nonvaso.rds", FORMULA_ovl2_vaso)

nonvaso_METADF0 <- rbind(
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_nonvaso.rds") %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_nonvaso.rds") %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_nonvaso.rds") %>% mutate("dataset"="AUMC"))
nonvaso_METADF_AKID <- nonvaso_METADF0 %>% subset(outcome=="outcome_KDIGO_inc_or_death")
nonvaso_METADF_AKI <- nonvaso_METADF0 %>% subset(outcome=="outcome_KDIGO_inc")
nonvaso_METADF_HD <- nonvaso_METADF0 %>% subset(outcome=="outcome_new_dial")
nonvaso_METADF_D <- nonvaso_METADF0 %>% subset(outcome=="death_in_7d")
nonvaso_METADF_HDD <- nonvaso_METADF0 %>% subset(outcome=="outcome_HDD_in7d")

nonvaso_METARES_AKID <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = nonvaso_METADF_AKID)
nonvaso_METARES_AKI <-rma(yi = Estimate, sei = Std.Error, method = "REML", data = nonvaso_METADF_AKI)
nonvaso_METARES_HD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = nonvaso_METADF_HD)
nonvaso_METARES_D <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = nonvaso_METADF_D)
nonvaso_METARES_HDD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = nonvaso_METADF_HDD)

METAF(nonvaso_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(A) AKI development/progression (No-vasopressor)")
nonvaso_METARES_AKI
nonvaso_METADF_AKI %>% dplyr::select(dataset, OR, LCI, UCI, 'Pr(>|z|)') %>% remove_rownames()
```


\_\_

#### 12. Firth's regression -\> forest plot.

In some subgroup analyses, outcomes only developed one group. Then, we
couldn't estimate odds ratio. Therefore, we estimated the ratio using
Firth's regression

```{r ovlp Firth method, warning=F, message=F}
#Firth's method function
library(logistf) #install.packages("logistf")
DF <- readRDS("wgt_man_Ovlp_MIMIC3_base12.rds")
DF$drug_type <- DF$drug_type %>% factor() %>% relevel(, ref = "NCC")
saveRDS(DF,"wgt_man_Ovlp_MIMIC3_base12.rds")
#logistf(formula = as.formula("outcome_KDIGO_inc ~ drug_type"), data  = readRDS("wgt_man_Ovlp_MIMIC3_base12.rds"), weights = ovlp_wgt)

OVLP_OR_F <- function(DF, FORM, OUTCOME, TITLE){
fit <- logistf(formula = as.formula(paste0(OUTCOME," ~ drug_type")), data  = DF, weights = ovlp_wgt)
fit %>% summary() %>% print()
est<-coef(fit)["drug_typeI/C"]
ci<-confint(fit)["drug_typeI/C", ]
summary1 <- data.frame(Estimate = est, Std.Error = (ci[2] - ci[1]) / (2 * 1.96), lwr=ci[1], upr=ci[2], 
                       study=TITLE, outcome=OUTCOME)
svy_design <- svydesign(~1, data = DF %>% as.data.frame(), weights = DF$ovlp_wgt)
fmla <- as.formula(paste("~", OUTCOME))
summary1 <- summary1 %>% mutate("pts"= svytable(fmla, svy_design) %>% as.data.frame() %>% .$Freq %>% sum(),
                                "events"=svytable(fmla, svy_design) %>% as.data.frame() %>% filter(.data[[OUTCOME]]==T) %>% .$Freq %>% sum())
summary1
}

FP2_F <- function(RDS, FORM,  OUTCOME, TITLE){
OR_RES_F <- OVLP_OR_F(readRDS(RDS), FORM, OUTCOME, TITLE) %>% 
  mutate("events_percentage"=events/sum(.$event), "pts_percentage"=pts/sum(.$pts))
saveRDS(OR_RES_F, paste0("ORRES_F_",RDS))}



### Start with each assessment
## Subgroup with AKI at treatment start -> AKI progression in mimic3
FP2_F("wgt_man_Ovlp_MIMIC3_base12.rds", FORMULA_ovl2, "outcome_KDIGO_inc", "AKI progression")

base12_METADF_F0 <- rbind( #Firth method only used for MIMIC3
  readRDS("ORRES_F_wgt_man_Ovlp_MIMIC3_base12.rds") %>% dplyr::select(Estimate, Std.Error, outcome, pts, events) %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_base12.rds") %>% dplyr::select(Estimate, Std.Error, outcome, pts, events) %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_base12.rds") %>% dplyr::select(Estimate, Std.Error, outcome, pts, events) %>%mutate("dataset"="AUMC"))

base12_METADF_F_AKI <- base12_METADF_F0 %>% subset(outcome=="outcome_KDIGO_inc")
base12_METARES_F_AKI <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = base12_METADF_F_AKI)

base12_METARES_F_AKI
SCALEA4<-c(0.01, 1, 16)
SCALEB4 <- c(-14,8.5)
SCALEC4 <- c(-8,-5.5)
METAF(base12_METARES_F_AKI, SCALEA4, SCALEB4, SCALEC4, "(B) AKI progression (with AKI at treatment start)")

## Subgroup without AKI at treatment start -> RRT in mimic4
DFbase <- readRDS("wgt_man_Ovlp_MIMIC4_base0.rds")
DFbase$drug_type <- DFbase$drug_type %>% factor() %>% relevel(, ref = "NCC")
saveRDS(DFbase,"wgt_man_Ovlp_MIMIC4_base0.rds")
FP2_F("wgt_man_Ovlp_MIMIC4_base0.rds", FORMULA_ovl2, "outcome_new_dial", "hemodialysis")

base0_METADF_F0 <- rbind( #Firth method only used for MIMIC4
  readRDS("ORRES_wgt_man_Ovlp_MIMIC3_base0.rds") %>% dplyr::select(Estimate, Std.Error, outcome, pts, events) %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_F_wgt_man_Ovlp_MIMIC4_base0.rds") %>% dplyr::select(Estimate, Std.Error, outcome, pts, events) %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_base0.rds") %>% dplyr::select(Estimate, Std.Error, outcome, pts, events) %>%mutate("dataset"="AUMC"))

base0_METADF_F_HD <- base0_METADF_F0 %>% subset(outcome=="outcome_new_dial")
base0_METARES_F_HD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = base0_METADF_F_HD)

base0_METARES_F_HD
METAF(base0_METARES_F_HD, SCALEA4, SCALEB4, SCALEC4, "(A) RRT-intervention (without AKI at treatment start)")

## Subgroup with AKI at treatment start -> RRT in mimic3
DFbase <- readRDS("wgt_man_Ovlp_MIMIC3_base12.rds")
DFbase$drug_type <- DFbase$drug_type %>% factor() %>% relevel(, ref = "NCC")
saveRDS(DFbase,"wgt_man_Ovlp_MIMIC3_base12.rds")
FP2_F("wgt_man_Ovlp_MIMIC3_base12.rds", FORMULA_ovl2, "outcome_new_dial", "hemodialysis")

base12_METADF_F0 <- rbind( #Firth method only used for MIMIC3
  readRDS("ORRES_F_wgt_man_Ovlp_MIMIC3_base12.rds") %>% dplyr::select(Estimate, Std.Error, outcome, pts, events) %>% mutate("dataset"="MIMIC-III"),
  readRDS("ORRES_wgt_man_Ovlp_MIMIC4_base12.rds") %>% dplyr::select(Estimate, Std.Error, outcome, pts, events) %>% mutate("dataset"="MIMIC-IV"),
  readRDS("ORRES_wgt_man_Ovlp_AUMC_base12.rds") %>% dplyr::select(Estimate, Std.Error, outcome, pts, events) %>%mutate("dataset"="AUMC"))

base12_METADF_F_HD <- base12_METADF_F0 %>% subset(outcome=="outcome_new_dial")
base12_METARES_F_HD <- rma(yi = Estimate, sei = Std.Error, method = "REML", data = base12_METADF_F_HD)

base12_METARES_F_HD
METAF(base12_METARES_F_HD, SCALEA4, SCALEB4, SCALEC4, "(A) RRT-intervention (with AKI at treatment start)")



#export
#subgroup main
tiff("Figure 4 (subgroup AKI).tif", 
     width = 6, 
     height = 8,     # Tall file to fit 3 plots vertically
     units = "in", 
     res = 300, 
     compression = "lzw")
par(mfrow = c(2, 1))
METAF(base0_METARES_AKI, SCALEA1, SCALEB1, SCALEC1, "(A) AKI development (without AKI at treatment start)")
METAF(base12_METARES_F_AKI, SCALEA4, SCALEB4, SCALEC4, "(B) AKI progression (with AKI at treatment start)")
dev.off()

#export wo AKI
tiff("eFigure 4 (secondary wo AKI).tif", 
     width = 6, 
     height = 8,     
     units = "in", 
     res = 300, 
     compression = "lzw")
par(mfrow = c(3, 1))
METAF(base0_METARES_F_HD, SCALEA4, SCALEB4, SCALEC4, "(A) RRT-intervention (without AKI at treatment start)")
METAF(base0_METARES_D, SCALEA1, SCALEB1, SCALEC1, "(B) Death (without AKI at treatment start)")
METAF(base0_METARES_HDD, SCALEA1, SCALEB1, SCALEC1, "(C) RRT-intervention or death (without AKI at treatment start)")
dev.off()

#export w AKI
tiff("eFigure 5 (secondary w AKI).tif", 
     width = 6, 
     height = 8,     
     units = "in", 
     res = 300, 
     compression = "lzw")
par(mfrow = c(3, 1))
METAF(base12_METARES_F_HD, SCALEA4, SCALEB4, SCALEC4, "(A) RRT-intervention (with AKI at treatment start)")
METAF(base12_METARES_D, SCALEA1, SCALEB1, SCALEC1, "(B) Death (with AKI at treatment start)")
METAF(base12_METARES_HDD, SCALEA1, SCALEB1, SCALEC1, "(C) RRT-intervention or death (with AKI at treatment start)")
dev.off()
```

\_\_

#### 13. Summary of subgroup analysis

```{r summary, fig.width=4.5,fig.height=3.5}
SCALEAsub<-c(0.25, 1, 4)
SCALEBsub <- c(-2.8,3.5)

SCALEAsub2<-c(0.1, 1, 10)
SCALEBsub2 <- c(-5.5, 6)

METAF2 <- function(METARES, AAA, BBB,TITLE){
metafor::forest(METARES,  atransf=exp, at=log(AAA), slab = dataset,
       xlim=BBB, 
       #ilab=cbind(round(pts, digits=1), round(events, digits=1)), 
       #ilab.lab=c("Subjects","Events"), ilab.pos = 2,
       #ilab.xpos=CCC,
       cex=0.85, cex.axis=0.7, annotate=T,
       header="", xlab="Odds ratio", mlab="Overall", shade=TRUE, 
       main=TITLE, adj=0)
}
METAF2(base0_METARES_AKI, SCALEAsub2, SCALEBsub2,  "no AKI")
METAF2(base12_METARES_F_AKI, SCALEAsub2, SCALEBsub2, "with AKI") #Filth!!!

METAF2(Young_METARES_AKI, SCALEAsub, SCALEBsub, "Age < 60y")
METAF2(Old_METARES_AKI, SCALEAsub, SCALEBsub, "Age 60y or older")

METAF2(Male_METARES_AKI, SCALEAsub, SCALEBsub, "Male")
METAF2(Female_METARES_AKI, SCALEAsub, SCALEBsub, "Female")

METAF2(surg_METARES_AKI, SCALEAsub, SCALEBsub, "Surgical unit")
METAF2(nonsurg_METARES_AKI, SCALEAsub, SCALEBsub, "Non-surgical unit")

METAF2(Lsirs_METARES_AKI, SCALEAsub, SCALEBsub, "SIRS<2")
METAF2(Hsirs_METARES_AKI, SCALEAsub, SCALEBsub, "SIRS=2 or higher")

METAF2(bc_METARES_AKI, SCALEAsub, SCALEBsub, "with pre-blood culture")
METAF2(nonbc_METARES_AKI, SCALEAsub, SCALEBsub, "no pre-blood culture")

METAF2(vc_METARES_AKI, SCALEAsub, SCALEBsub, "Vancomycin treated")
METAF2(novc_METARES_AKI, SCALEAsub, SCALEBsub, "No vancomycin treatment")

METAF2(vaso_METARES_AKI, SCALEAsub, SCALEBsub, "Vasopressor treated")
METAF2(nonvaso_METARES_AKI, SCALEAsub, SCALEBsub, "No vasopressor")

#export
tiff("eFigure 6 (various subgroup).tif", 
     width = 16, 
     height = 16,     # Tall file to fit 3 plots vertically
     units = "in", 
     res = 300, 
     compression = "lzw")
par(mfrow = c(4, 4))
METAF2(Young_METARES_AKI, SCALEAsub, SCALEBsub, "Age < 60y")
METAF2(Old_METARES_AKI, SCALEAsub, SCALEBsub, "Age 60y or older")
METAF2(Male_METARES_AKI, SCALEAsub, SCALEBsub, "Male")
METAF2(Female_METARES_AKI, SCALEAsub, SCALEBsub, "Female")
METAF2(surg_METARES_AKI, SCALEAsub, SCALEBsub, "Surgical unit")
METAF2(nonsurg_METARES_AKI, SCALEAsub, SCALEBsub, "Non-surgical unit")
METAF2(Lsirs_METARES_AKI, SCALEAsub, SCALEBsub, "SIRS<2")
METAF2(Hsirs_METARES_AKI, SCALEAsub, SCALEBsub, "SIRS=2 or higher")
METAF2(bc_METARES_AKI, SCALEAsub, SCALEBsub, "with pre-blood culture")
METAF2(nonbc_METARES_AKI, SCALEAsub, SCALEBsub, "no pre-blood culture")
METAF2(vc_METARES_AKI, SCALEAsub, SCALEBsub, "Vancomycin treated")
METAF2(novc_METARES_AKI, SCALEAsub, SCALEBsub, "No vancomycin treatment")
METAF2(vaso_METARES_AKI, SCALEAsub, SCALEBsub, "Vasopressor treated")
METAF2(nonvaso_METARES_AKI, SCALEAsub, SCALEBsub, "No vasopressor")
dev.off()
```


```{r darren method, include=F}
#PSM with MIMIC4
matched_MIMIC4 <- matchit(data=comb_DF2 %>% subset(dataset=="miiv"), FORMULA0, method="nearest", caliper=0.2, distance="glm", link="logit", estimand="ATT", replace=F, ratio=1)
DM_MIMIC4 <- comb_DF2 %>% subset(dataset=="miiv") %>% mutate("distance"=matched_MIMIC4$distance)

matched_MIMIC3 <- matchit(data=comb_DF2 %>% subset(dataset=="MIMIC3"), FORMULA0, method="nearest", caliper=0.2, distance="glm", link="logit", estimand="ATT", replace=F, ratio=1)
DM_MIMIC3 <- comb_DF2 %>% subset(dataset=="MIMIC3") %>% mutate("distance"=matched_MIMIC3$distance)

matched_AUMC <- matchit(data=comb_DF2 %>% subset(dataset=="AUMC"), FORMULA0, method="nearest", caliper=0.2, distance="glm", link="logit", estimand="ATT", replace=F, ratio=1)
DM_AUMC <- comb_DF2 %>% subset(dataset=="AUMC") %>% mutate("distance"=matched_AUMC$distance)

DM_FORMULA <- "outcome_KDIGO_inc ~ drug01 + distance + age_cat + sex + dep_type2 + sirs + pre_blood_culture + treat_van + vasopressor + base_crea + near_crea + base_KDIGO"

DMDF <-
rbind(
  glm(as.formula(DM_FORMULA), data=DM_MIMIC3) %>% broom::tidy() %>% subset(term=="drug01") %>% mutate(dataset="MIMIC3"),
  glm(as.formula(DM_FORMULA), data=DM_MIMIC4) %>% broom::tidy() %>% subset(term=="drug01") %>% mutate(dataset="MIMIC4"),
  glm(as.formula(DM_FORMULA), data=DM_AUMC) %>% broom::tidy() %>% subset(term=="drug01") %>% mutate(dataset="AUMC")
  )
DMDF$dataset <- DMDF$dataset %>% factor(levels = c("AUMC", "MIMIC4", "MIMIC3"))
ggplot(DMDF, aes(exp(estimate), dataset))+geom_vline(xintercept = 1, linetype = "dashed", color = "gray50") +
  geom_errorbarh(aes(xmin = exp(estimate - 1.96 * std.error), 
                     xmax = exp(estimate + 1.96 * std.error)), 
                 height = 0.15, color = "black", linewidth = 0.7) +
  geom_point(size=3.5)+theme_classic()+ xlim(c(0.5,2))+
  labs(x = "Log Odds / Estimate", 
       y = "Dataset", 
       title = "Forest Plot of drug01 Effect Across Datasets") +ggtitle("AKI development/progression (<- glm with confounders&PS)")
```
