---
title: "mimic3"
output:
  html_document:
    toc: true
    toc_depth: 3
    theme: united
  pdf_document: 
    toc: true
    toc_depth: 3
  word_document:
    toc: true
    toc_depth: '3'
date: "`r Sys.Date()`"
editor_options:
  markdown:
    wrap: 72
---

# [**MIMIC3**]{.underline}

### MIMIC3 data managing

#### 1. Base settings of R and data

```{r download import, echo=T, warning=F, message= F}
library(ricu) #install.packages("ricu")
library(fst)#install.packages("fst")
library(utils)
library(tidyverse)
library(units)
library(dplyr)
library(here)
library(gtsummary) #install.packages("gtsummary")
#install.packages("tinytex")
#tinytex::install_tinytex()
#Sys.which("pdflatex")

###Set folder path
Sys.setenv(RICU_DATA_PATH="C:\\Users\\aomura\\Desktop\\ricu2") #C:\\Users\\aomura\\OneDrive - Oregon Health & Science University\\Desktop\\ricu2
dir<-paste0(ricu::data_dir(),"\\mimic")

###Set username and password (Already done -> not run this time)
#Sys.setenv(RICU_PHYSIONET_USER="aomura")
#Sys.setenv(RICU_PHYSIONET_PASS="") #<- Hidden

###Download and import mimic3 data (Already done -> not run this time)
#download_src("mimic",data_dir=dir,user="aomura", pass="", verbose=TRUE)
#import_src("mimic", data_dir=dir, force=T, verbose=T)

###Attach mimic3 data (then you can check by ricu::src_data_avail())
ricu::attach_src("mimic", data_dir = dir, assign_env = NULL)
src  <- "mimic"
detach("package:ricu", unload = TRUE)
```

**\_\_**

#### **2. Extract the data about carbapenems usage**

##### Collect data of carbapenems injection

```{r penem collect}
##collect data of carbapenems injection
penem_names <- "penem|PENEM|primaxin|Primaxin|PRIMAXIN|merrem|Merrem|MERREM|meronem|Meronem|MERONEM|invanz|Invanz|INVANZ|doribax|Doribax|DORIBAX|vabomere|Vabomere|VABOMERE|recarbrio|Recarbrio|RECABRIO"
received_carbapenems <- ricu::mimic$prescriptions[grep(penem_names, ricu::mimic$prescriptions$drug, ignore.case=TRUE),] 

#The data had no injection "time". Since the average of injection time on mimic4 was PM0 or 1, add 12h to the injection data.  
received_carbapenems$startdate2 <- received_carbapenems$startdate + dminutes(780)

carbapenems <- received_carbapenems %>% dplyr::select(subject_id, hadm_id, icustay_id, drug, formulary_drug_cd, gsn,route, dose_val_rx, startdate2, enddate) %>% filter(hadm_id %in% (read.csv("ADMISSIONS_true_mimic3.csv") %>% .$hadm_id))

#check injections
carbapenem_summary <- carbapenems %>% group_by(drug) %>% reframe(Subjects_Receiving=n_distinct(subject_id), Unique_hadm_admissions=n_distinct(hadm_id))
carbapenem_summary %>% rbind(c("original","",sum(.$Unique_hadm_admissions)),.)
```

```{r penem check garbage, include=F}
##collect carbapenems orders from input events
#t <- as.data.frame(ricu::mimic$d_items)
#t %>% filter(str_detect(label,".*penem")) %>% head(3)
#t %>% filter(str_detect(label,".*penem")) %>% .$label %>% unique() 
#t %>% filter(str_detect(label,".*penem")) %>% .$dbsource %>% unique() 

##collect carbapenems data from inputevents
##first check itemid of injection of antibiotics 
#u <- t %>% filter((linksto=="inputevents_mv") & (str_detect(label,".*penem")==TRUE))
#carbapenem_itemids <- unlist(u$itemid)
#imipenem_itemid <- 225876
#imipenem_cilastatins <- received_imipenem_cilastatin %>% dplyr::select(subject_id, hadm_id, icustay_id, drug, formulary_drug_cd, gsn,route, dose_val_rx, startdate, enddate)
#received_imipenem_cilastatin <- ricu::mimic$prescriptions[grep("lastatin", ricu::mimic$prescriptions$drug, ignore.case=T),]
#received_imipenem_cilastatin <- received_imipenem_cilastatin %>% mutate(imipenem_cilastatin=TRUE)
#received_carbapenems <- received_carbapenems %>% mutate(carbapenem=TRUE)
```

\_\_

##### Check the counts of hospital admission (hadm) which containing ICU-carbabapenems usage

```{r get basic data}
###Counts hospital admission (hadm) which includes ICU-carbabapenem use
ICU_carbapenem_hadmID <- carbapenems %>% filter(!is.na(icustay_id)) %>% .$hadm_id %>% unique()
c("hadm counts with ICU-carbabapenem usage", ICU_carbapenem_hadmID %>% unique() %>% length())
```

\_\_

##### Obtain 1st (earliest)-carbapenems usage in the hospital admission of each patient (-\> number of treated patients)

##### Then, exclude some of non-eligible patients.

```{r get basic data_1}
###Get 1st(earliest)-carbapenem in the hadm (I decided not icustay_id but hadm_id!!!)
#hadm_id not exists in "ICU_carbapenem_hadmID" means hadm w/o ICU-carbapenem -> removed.
#Subjects with "icustay_id = NA". Those may mean 1st-carbapenem (1st-ABX) was before ICU. (Not w/o-carbapenem during ICU admission, because I already filtered those by "hadm_id %in% ICU_carbapenem_hadmID" in the code). Leave it now.
carbapenem0 <- carbapenems %>% group_by(hadm_id) %>% mutate(hadm_first_carbapenem_start=min(startdate2)) %>%
                              filter(hadm_first_carbapenem_start==startdate2) %>% 
                              dplyr::select(-startdate2, -enddate) %>% filter(hadm_id %in% ICU_carbapenem_hadmID & !is.na(icustay_id)) %>%  
                              distinct()
c("prior penems usage excluded", carbapenem0$hadm_id %>% unique() %>% length())

###Delete some duplicates (different dosage/name in the same day same patients)
carbapenem0$drug_type <- ifelse(carbapenem0$drug=="Imipenem-Cilastatin", "IMI", 
                                 ifelse(carbapenem0$drug=="Imipenem-Cilastatin *NF*", "IMI", "non_IMI"))
duplicated_rows <- duplicated(carbapenem0[, c("hadm_id", "drug_type")])
carbapenem00 <- carbapenem0[!duplicated_rows, ]
c("duplicated injection excluded", carbapenem00$hadm_id %>% unique() %>% length())

###Some patients started imipenem/cilastatin and other carbapenem at the same day.Why??????. Delete those from both groups.
remain_id <- carbapenem00 %>% group_by(hadm_id) %>% summarise(n=n()) %>% filter(n<2) %>% .$hadm_id
carbapenem <- carbapenem00[carbapenem00$hadm_id %in% remain_id, ]
c("imi/cil_carbapenems_duplicated subjects excluded", carbapenem$hadm_id %>% unique() %>% length())
```

\_\_

#### **3. Extract the data about hospital/ICU admission**

```{r get basic data2}
###obtain admission time (intime) of hadm and ICU
hadm_intime <- ricu::load_src(ricu::mimic$admissions, hadm_id %in% carbapenem$hadm_id) %>% as.data.frame() %>%
                dplyr::select(hadm_id, admittime) %>% rename("hadm_time"=admittime)
ICU_intime <- ricu::load_src(ricu::mimic$icustays, hadm_id %in% carbapenem$hadm_id) %>% as.data.frame() %>% 
                dplyr::select(icustay_id, intime) %>% rename("ICU_admit_time"=intime)

###Add those admission time info to carbapenem_DF.
carbapenem_a <- carbapenem %>% left_join(hadm_intime, by="hadm_id") %>% left_join(ICU_intime, by="icustay_id") %>% distinct()

###ICUstay_id NA may mean first ABX was before ICU (not meaning not ICU admission as written above chunk). Delete those.
carbapenem_b <- carbapenem_a %>% filter(!is.na(icustay_id)) 

###Delete the patients who got 1st-ABX in the hadm before ICU admission
carbapenem_b1 <- carbapenem_b %>% mutate("sec_ICUadmit_to_abx"= hadm_first_carbapenem_start - ICU_admit_time) %>%
                  filter(sec_ICUadmit_to_abx>0) %>% dplyr::select(-sec_ICUadmit_to_abx)


carbapenem_b2<- carbapenem_b1 %>% subset(drug!="Meropenem Desensitization")

###check carbapenems number (per hadm_id!)
list(c("carbapenem usage hadm among PTs who experienced ICU", carbapenem  %>% nrow()),
     c("carbapenem before ICU in the hadm were excluded", carbapenem_b1 %>% nrow()),
       c("carbapenem with desensitization excluded", carbapenem_b2 %>% nrow))
```
```{r group transfer, message=F, warning=F}
carbapenems$drug_type <- ifelse(carbapenems$drug=="Imipenem-Cilastatin", "IMI", 
                        ifelse(carbapenems$drug=="Imipenem-Cilastatin *NF*", "IMI", "non_IMI"))
first_IMI <- carbapenems %>% filter(drug_type=="IMI") %>% group_by(hadm_id) %>% filter(startdate2==min(startdate2)) %>%
                              rename("hadm_1st_time_IMI"=startdate2) %>% filter(hadm_id %in% ICU_carbapenem_hadmID & !is.na(icustay_id)) %>%  
                              distinct() %>% dplyr::select(hadm_id, hadm_1st_time_IMI) 
first_nonIMI <- carbapenems %>% filter(drug_type=="non_IMI") %>% group_by(hadm_id) %>% filter(startdate2==min(startdate2)) %>%
                              rename("hadm_1st_time_nIMI"=startdate2) %>% filter(hadm_id %in% ICU_carbapenem_hadmID & !is.na(icustay_id)) %>%  
                              distinct() %>% dplyr::select(hadm_id, hadm_1st_time_nIMI) 

carbapenem_b3 <- carbapenem_b2 %>% left_join(first_IMI, by="hadm_id") %>% left_join(first_nonIMI, by="hadm_id") %>% distinct()
carbapenem_b3$time_switch_group0 <- abs(difftime(carbapenem_b3$hadm_1st_time_nIMI, carbapenem_b3$hadm_1st_time_IMI, units = "hours")) %>% as.numeric() %>% abs()

carbapenem_b3$time_switch_group <- ifelse(is.na(carbapenem_b3$time_switch_group0), 168, 
                                   ifelse(carbapenem_b3$time_switch_group0>168, 168, carbapenem_b3$time_switch_group0))
carbapenem_b4 <- carbapenem_b3 %>% filter(time_switch_group>24)

c("carbapenem w/o group transfer within 24h", carbapenem_b4  %>% nrow())
```
\_\_

#### **4. Collect creatinine data to exclude patients without appropriate creatinine assessment**

```{r creatinine}
###obtain creatinine values (itemid=50912)
creatinine <- ricu::load_src(ricu::mimic$labevents, itemid ==50912 & hadm_id %in% carbapenem$hadm_id) %>% 
                as.data.frame() %>% 
              dplyr::select(-itemid, -valuenum, -valueuom, -flag) %>% 
                rename("creatinine"=value) #manually collect to obtain raw time

###some data are like "less than 0.1" and cannot be tranformed to numeric. Delete those.
creatinine$creatinine <- creatinine$creatinine %>% as.numeric()
creatinine <- creatinine %>% filter(!is.na(creatinine))

###Collect 1st(earliest) creatinine value in the hadm. 
###Assess the measurement time from ICU admission.
###1st_creatinine later than ICU admission means no creatinine measurement before ICU. Deleted.
#exclude later than 1st-ABX would be better?????????) 
First_creatinine <- creatinine %>% group_by(hadm_id) %>% summarise(first_Crea_time=min(charttime))
carbapenem_c <- carbapenem_b4 %>% left_join(First_creatinine, by="hadm_id") %>% distinct() %>% 
                 mutate("Crea_to_ICUadmit"=ICU_admit_time-first_Crea_time) %>% 
                  filter(Crea_to_ICUadmit>0) %>% dplyr::select(-Crea_to_ICUadmit)

###Collect last(latest) creatinine value in the hadm. 
###Assess the measurement time after first_ABX.
###last creatinine earlier 1st_ABX means follow creatinine up after ABX -> deleted for now.
Last_creatinine <- creatinine %>% group_by(hadm_id) %>% summarise(Last_Crea_time=max(charttime))
carbapenem_d <- carbapenem_c %>% left_join(Last_creatinine, by="hadm_id")  %>% distinct() %>%
                 mutate("Crea_to_Abx"=hadm_first_carbapenem_start-Last_Crea_time) %>% 
                  filter(Crea_to_Abx<0) %>% dplyr::select(-Crea_to_Abx)
carbapenem_d$time_ICUadmit_to_abx <- difftime(carbapenem_d$hadm_first_carbapenem_start, carbapenem_d$ICU_admit_time, units = "hours")

###Check the number of remained subjects
list(
c("No Crea measurement in the hadm before ICU was excluded", carbapenem_c %>% nrow),
c("No Crea measurement in the hadm after Abx was excluded", carbapenem_d %>% nrow))
```

**\_\_**

#### **5. Collect data about patients characteristics**

##### Age and sex

```{r age and sex data, message=FALSE}
#Collect and add age and sex data
dict <- ricu::load_dictionary(src="mimic")
#dict %>% as.data.frame()
age <- ricu::load_concepts("age", src="mimic") %>% as.data.frame() 
age$age_group <- ifelse(age$age<18, NA,
                  ifelse(age$age<40, "18-39",
                   ifelse(age$age<50, "40-49",
                    ifelse(age$age<60, "50-59",
                     ifelse(age$age<70, "60-69",
                      ifelse(age$age<80, "70-79", "80+"))))))
age$age_cat <- ifelse(age$age_group=="18-39", 30, 
                ifelse(age$age_group=="40-49", 45,
                 ifelse(age$age_group=="50-59", 55,
                  ifelse(age$age_group=="60-69", 65,
                   ifelse(age$age_group=="70-79", 75,
                    ifelse(age$age_group=="80+", 85, NA))))))
sex <- ricu::load_concepts("sex", src="mimic") %>% as.data.frame()
bmi <- ricu::load_concepts("bmi", src="mimic") %>% as.data.frame()
```

\_\_

##### Comorbidity from ICD9 records (chronic heart failure, diabetes, chronic kidney disease, hypertension)

```{r comorbidities, warning=F}
#  below from https://github.com/MIT-LCP/mimic-code/blob/main/mimic-iii/concepts/comorbidity/elixhauser_quan.sql
# -- This code calculates the Elixhauser comorbidities as defined in Quan et. al 2009:
#   -- Quan, Hude, et al. "Coding algorithms for defining comorbidities in
# -- ICD-9-CM and ICD-10 administrative data." Medical care (2005): 1130-1139.
# --  https://www.ncbi.nlm.nih.gov/pubmed/16224307
# 
# -- Quan defined an "Enhanced ICD-9" coding scheme for deriving Elixhauser
# -- comorbidities from ICD-9 billing codes. This script implements that calculation.
# 
# -- The logic of the code is roughly that, if the comorbidity lists a length 3
# -- ICD-9 code (e.g. 585), then we only require a match on the first 3 characters.
# 
# -- This code derives each comorbidity as follows:
# --  1) ICD9_CODE is directly compared to 5 character codes
# --  2) The first 4 characters of ICD9_CODE are compared to 4 character codes
# --  3) The first 3 characters of ICD9_CODE are compared to 3 character codes

icd9_df <- data.frame(ricu::load_id(ricu::mimic$diagnoses_icd))

#chronic heart failure
chf_codes<-c("39891","40201","40211","40291","40401","40403","40411","40413","40491","40493")
chf_codes3<-c("428") #Broad "heart failre"
chf_codes4<-c("4254","4255","4257","4258","4259")
icd9_df <- icd9_df %>% mutate(chf=ifelse(icd9_code %in% chf_codes, TRUE, FALSE))
icd9_df <- icd9_df %>% mutate(chf=ifelse(str_sub(icd9_code,1,3) %in% chf_codes3, TRUE, chf))
icd9_df <- icd9_df %>% mutate(chf=ifelse(str_sub(icd9_code,1,4) %in% chf_codes4, TRUE, chf))

#DM (manually collected)
dm_codes <- c("24900","24901","24910","24911","24920","24921","24930","24931","24940","24941","24950","24951","24960","24961","24970","24971","24980","24981","24990","24991","25000","25001","25002","25003","25010","25011","25012","25013","25020","25021","25022","25023","25030","25031","25032","25033","25040","25041","25042","25043","25050","25051","25052","25053","25060","25061","25062","25063","25070","25071","25072","25073","25080","25081","25082","25083","25090","25091","25092","25093","2535","3572","36201","36202","36203","36204","36205","36206","36207","36641","5881","7751")
icd9_df <- icd9_df %>% mutate(dm=ifelse(icd9_code %in% dm_codes, TRUE, FALSE))

#CKD
ckd_codes <- c('28521','40301','40311','40391','40402','40403','40412','40413','40492','40493')
ckd_codes3 <- c('585','586', '587')
ckd_codes4 <- c('5880','V420','V451', '5889', '7944')
icd9_df<-icd9_df %>% mutate(ckd=ifelse(icd9_code %in% ckd_codes, TRUE, FALSE))
icd9_df<-icd9_df %>% mutate(ckd=ifelse(str_sub(icd9_code,1,3) %in% ckd_codes3, TRUE, ckd))
icd9_df<-icd9_df %>% mutate(ckd=ifelse(str_sub(icd9_code,1,4) %in% ckd_codes4, TRUE, ckd))

#hypertension
htn_codes <- c()
htn_codes3 <- c("401","402","403","404","405")
htn_codes4 <- c()
icd9_df<-icd9_df%>%mutate(htn=ifelse(icd9_code%in%htn_codes,TRUE,FALSE))
icd9_df <- icd9_df %>% mutate(htn=ifelse(str_sub(icd9_code,1,3) %in% htn_codes3, TRUE, FALSE))
icd9_df<-icd9_df%>%mutate(htn=ifelse(str_sub(icd9_code,1,4)%in%htn_codes4,TRUE,htn))

###combine
icd9_df <- icd9_df %>% group_by(icustay_id) %>% summarize(ph_htn=(sum(htn)>0), ph_dm=(sum(dm)>0), ph_chf=(sum(chf)>0), ph_ckd=(sum(ckd)>0))
```

####Check cardiac surgery before Abx using ICD code
```{r Check cardiac surgery before Abx using ICD code}
CPTE <- ricu::mimic$cptevents %>% as.data.frame()  %>% filter(hadm_id %in% carbapenem_d$hadm_id) 
PICD9 <- ricu::mimic$procedures_icd %>% as.data.frame() %>% filter(hadm_id %in% carbapenem_d$hadm_id) %>% 
         left_join(ricu::mimic$d_icd_procedures %>% as.data.frame() %>% dplyr::select(icd9_code, short_title, long_title), by="icd9_code") %>% 
          distinct() %>% dplyr::select(-seq_num)
#No operation date!!!!
```
\_\_

##### **Codes for checking the current progression**

##### There are duplicated patients (same patient, different hospital/ICU admission)

##### -\> But, I didn't care those duplication. Use those as different patients/subjects.

```{r Codes for checking the current progression}
list(c("counts of ICUstay", carbapenem_d$icustay_id %>% unique() %>% length()),
      c("counts of hadm", carbapenem_d$hadm_id %>% unique() %>% length()),
       c("counts of patients", carbapenem_d$subject_id %>% unique() %>% length())) #But I don't care duplicated patients
```

**\_\_**

#### **6. Collect SOFA data at initiation of 1st-carbapenems treatment**

##### -\> referring to SOFA data between -7 to -0 day until 1st-carbapenems treatment

```{r base sofa}
###SOFA score at time of 1st_ABX. (It takes long time. So, the first 3 lines are silenced) 
#sofa <- ricu::load_concepts("sofa", src="mimic") %>% as.data.frame() 
#saveRDS(sofa,"sofa.rds")
sofa<-readRDS("sofa.rds")

###Calculate the time from ICU_admission to 1st_ABX. Add those data in SOFA_DF
#carbapenem_d$time_ICUadmit_to_abx_days <- difftime(carbapenem_d$hadm_first_carbapenem_start, carbapenem_d$ICU_admit_time, units="days") #overwrite
sofa2 <- sofa %>% left_join(carbapenem_d %>% dplyr::select(icustay_id, time_ICUadmit_to_abx), by="icustay_id") %>% filter(!is.na(time_ICUadmit_to_abx)) %>% distinct()

###Collect the SOFA scores which were closest to 1st-ABX time in each subjects
sofa2$proximality_to_abx <- sofa2$charttime - sofa2$time_ICUadmit_to_abx
sofa3 <- sofa2 %>% subset(proximality_to_abx>-168.1 & proximality_to_abx<0.01) %>% group_by(icustay_id) %>% slice_max(order_by = proximality_to_abx)

#sofa_cns <- ricu::load_concepts("sofa_cns", src="mimic") %>% as.data.frame() 
#saveRDS(sofa_cns,"sofa_cns.rds")
sofa_cns <- readRDS("sofa_cns.rds") %>% as.data.frame() %>% filter(icustay_id %in% carbapenem_d$icustay_id) 
sofa_cns2 <- sofa_cns %>% left_join(carbapenem_d %>% dplyr::select(icustay_id, time_ICUadmit_to_abx), by="icustay_id") %>% filter(!is.na(time_ICUadmit_to_abx)) %>% distinct()
sofa_cns2$proximality_to_abx <- sofa_cns2$charttime - sofa_cns2$time_ICUadmit_to_abx
sofa_cns3 <- sofa_cns2 %>% subset(proximality_to_abx>-168.1 & proximality_to_abx<0.01) %>% group_by(icustay_id) %>% slice_max(order_by = proximality_to_abx)

#sofa_renal <- ricu::load_concepts("sofa_renal", src="mimic") %>% as.data.frame()
#saveRDS(sofa_renal,"sofa_renal.rds")
sofa_renal <- readRDS("sofa_renal.rds") %>% as.data.frame() %>% filter(icustay_id %in% carbapenem_d$icustay_id)
sofa_renal2 <- sofa_renal %>% left_join(carbapenem_d %>% dplyr::select(icustay_id, time_ICUadmit_to_abx), by="icustay_id") %>% filter(!is.na(time_ICUadmit_to_abx)) %>% distinct()
sofa_renal2$proximality_to_abx <- sofa_renal2$charttime - sofa_renal2$time_ICUadmit_to_abx
sofa_renal3 <- sofa_renal2 %>% subset(proximality_to_abx>-168.1 & proximality_to_abx<0.01) %>% group_by(icustay_id) %>% slice_max(order_by = proximality_to_abx)

#sep <- ricu::load_concepts("sep3", src="mimic") %>% as.data.frame()
#saveRDS(sep,"sep.rds")
sep <- readRDS("sep.rds") %>% as.data.frame() %>% filter(icustay_id %in% carbapenem_d$icustay_id)
sep2 <- sep %>% left_join(carbapenem_d %>% dplyr::select(icustay_id, time_ICUadmit_to_abx), by="icustay_id") %>% filter(!is.na(time_ICUadmit_to_abx)) %>% distinct()
sep2$proximality_to_abx <- sep2$charttime - sep2$time_ICUadmit_to_abx
sep3 <- sep2 %>% subset(proximality_to_abx>-168.1 & proximality_to_abx<0.01) %>% group_by(icustay_id) %>% slice_max(order_by = proximality_to_abx)

#sirs <- ricu::load_concepts("sirs", src="mimic") %>% as.data.frame()
#saveRDS(sirs,"sirs.rds")
sirs <- readRDS("sirs.rds") %>% as.data.frame() %>% filter(icustay_id %in% carbapenem_d$icustay_id)
sirs2 <- sirs %>% left_join(carbapenem_d %>% dplyr::select(icustay_id, time_ICUadmit_to_abx), by="icustay_id") %>% filter(!is.na(time_ICUadmit_to_abx)) %>% distinct()
sirs2$proximality_to_abx <- sirs2$charttime - sirs2$time_ICUadmit_to_abx
sirs3 <- sirs2 %>% subset(proximality_to_abx>-168.1 & proximality_to_abx<0.01) %>% group_by(icustay_id) %>% slice_max(order_by = proximality_to_abx)

#qsofa <- ricu::load_concepts("qsofa", src="mimic") %>% as.data.frame()
#saveRDS(qsofa,"qsofa.rds")
qsofa <- readRDS("qsofa.rds") %>% as.data.frame() %>% filter(icustay_id %in% carbapenem_d$icustay_id)
qsofa2 <- qsofa %>% left_join(carbapenem_d %>% dplyr::select(icustay_id, time_ICUadmit_to_abx), by="icustay_id") %>% filter(!is.na(time_ICUadmit_to_abx)) %>% distinct()
qsofa2$proximality_to_abx <- qsofa2$charttime - qsofa2$time_ICUadmit_to_abx
qsofa3 <- qsofa2 %>% subset(proximality_to_abx>-168.1 & proximality_to_abx<0.01) %>% group_by(icustay_id) %>% slice_max(order_by = proximality_to_abx)
```

\_\_

#### **7. Collect creatinine data to assess AKI stage at 1st_carbapenems (base AKI stage)**

1.  Definition of KDIGO-AKI stage is like
    [here](https://www.google.com/search?sca_esv=f3abac6c97ce75c7&rlz=1C1GCGZ_enUS1143US1143&sxsrf=AE3TifOebKzQqJs2WB9B1Mbqu_7235nM3A:1758676845480&udm=2&fbs=AIIjpHzuznnfRcKw6WJsjCzN2zWf55I9OrcLWiEzlPL8TiG0L_DqC0w_yKrYVnGrQTB16CZnNSIjQP6D4-nVGdJK4dmKLRGm2q9iZ8MYSZa5XlQjo8XFFjjLcCpEsAdvfdP2eMmNTRnjLAe6LpO7enjN3CzO0IZGs0dHi3xaS8ywMG8H3Y-YneaOlxKy7HvPxy8ZTOEG1cja32ItydtCnEy90dHS0m35sBM7E1emMfKrRBTBXFnBvXs&q=KDIGO+AKI&sa=X&ved=2ahUKEwjt9ZjlnfCPAxUNEzQIHXKvFEUQtKgLegQIFRAB&biw=2100&bih=1101&dpr=0.8){.uri}.
    Data of urine output in MIMIC is suspicious (like 3000ml/h). So,
    [**I completely ignored urine output in this
    study**]{.underline}**.**
2.  Min crea in -7d to 0d for 1st-carbapenem was defined as "base_crea"
3.  Crea_value nearest to the 1st_abx and before 1st abx was defined as
    "near_crea".
4.  Max_crea after 1st_abx and within 7d was defined as "max_crea".
5.  AKI stage at treatment was calculated with "base_crea" and
    "near_crea". AKI stage after treatment was calculated with
    "near_crea" and "max_crea".
6.  The crea chage over 0.3 mg/dl within 48h (-\> AKI stage 1) was also
    analyzed.

```{r base KDIGO creatinine}
###Start from creatinine data which obtained above (Basically those are not processed/filtered -> Fine to use.) 
#Put 1st_ABX data from carbapenem_DF and calculate time difference to each creatinine measurement.
#Erase crea after group transfer
creatinine_b <- creatinine %>% rename("Crea_time" = charttime) %>% left_join(carbapenem_d, by="hadm_id") %>% distinct() %>% 
  mutate("time_abx_to_Crea"=difftime(Crea_time, hadm_first_carbapenem_start, units = "hours")) %>% subset(time_abx_to_Crea<time_switch_group)

###Base crea is min crea during -7d to -0d until 1st_ABX.
#Extract base crea 
base_creatinine_value <- creatinine_b %>% filter(time_abx_to_Crea<0&time_abx_to_Crea>-168) %>% group_by(hadm_id) %>% summarise(base_creatinine=min(creatinine, na.rm=TRUE))

#Extract lowest crea between -48h to 0h
bef48min_creatinine_value <- creatinine_b %>% filter(time_abx_to_Crea<0&time_abx_to_Crea>-48) %>% group_by(hadm_id) %>% summarise(min_bef48_creatinine=min(creatinine, na.rm=TRUE))

#Extract nearest crea to 1st_abx (and before 1st_abx)
bef_near_creatinine_value <- creatinine_b %>% filter(time_abx_to_Crea<0&time_abx_to_Crea>-168) %>% group_by(hadm_id) %>%
                             filter(time_abx_to_Crea==min(time_abx_to_Crea)) %>% 
                             rename("near_crea"=creatinine) %>% dplyr::select(hadm_id, near_crea)

#Add base_crea and min48_crea to creatinine df  
creatinine_c <- creatinine_b %>% left_join(base_creatinine_value, by="hadm_id") %>% left_join(bef48min_creatinine_value, by="hadm_id") %>%  left_join(bef_near_creatinine_value, by="hadm_id") %>% filter(!is.na(base_creatinine)) %>% distinct()

###Check how many hadm have base creatinine. 
creatinine_c$hadm_id %>% unique() %>% length() %>% paste0("pts with creatinine = ", .) #It should be same as "counts of hadm" in the above chunk.
```

\_\_

```{r base creatinine assessment}
###Extract crea data bef 1st_abx (-7d to 0d)
bef_creatinine_c <- creatinine_c %>% filter(time_abx_to_Crea>-168, time_abx_to_Crea<0) %>% dplyr::select(hadm_id, base_creatinine, min_bef48_creatinine, near_crea) %>% distinct()

###calculate ratio and difference to base crea 
bef_creatinine_c$ratio_near_to_base <- bef_creatinine_c$near_crea / bef_creatinine_c$base_creatinine
bef_creatinine_c$diff_near_to_min48 <- bef_creatinine_c$near_crea - bef_creatinine_c$min_bef48_creatinine
  
###Convert to KDIGO stage
bef_creatinine_c$KDIGO_ratio <- ifelse(bef_creatinine_c$base_creatinine>4,3,
                                  ifelse(bef_creatinine_c$near_crea>4,3,
                                   ifelse(bef_creatinine_c$ratio_near_to_base>3,3,
                                    ifelse(bef_creatinine_c$ratio_near_to_base>2,2,
                                     ifelse(bef_creatinine_c$ratio_near_to_base>1.5,1,0)))))
bef_creatinine_c$KDIGO_dif <- ifelse(bef_creatinine_c$diff_near_to_min48>0.299, 1, 0)
bef_creatinine_c$KDIGO_crea <- pmax(bef_creatinine_c$KDIGO_ratio, bef_creatinine_c$KDIGO_dif)
```

##### **Assess AKI stage at initiation of carbapenems from dialysis data.**

1.  Collect dialysis data
2.  Assess whether the patients received dialysis before 1st_carbapenems
    treatment (-7 to -0 day)
3.  Whether the patients had received maintenance dialysis (before
    treatment) is not considered.

```{r base dialysis 0}
###Next, cellct dialysis event from d_items and output events.
###check ids for dialysis
CRRT1_item_labels <- grep("CVV", ricu::mimic$d_items$label, value=TRUE)
CRRT2_item_labels <- grep("CRR", ricu::mimic$d_items$label, value=TRUE)
CRRT3_item_labels <- grep("Dialys",ricu::mimic$d_items$label, value=TRUE)
RRTlabels <- c(CRRT1_item_labels, CRRT2_item_labels, CRRT3_item_labels)
RRTids <- ricu::mimic$d_items$itemid[ricu::mimic$d_items$label %in% RRTlabels]
RRTlabel <- ricu::mimic$d_items$label[ricu::mimic$d_items$itemid %in% RRTids]
d_RRTitems0 <- data.frame(item=RRTids, label=RRTlabel)
RRT_omits <- c("Site","Calcium","Dressing","Medication", "KCl","KCL","Access",
               "Heparin", "Catheter","Solution","Fluid", "GLUC","patient")
z <- paste(RRT_omits, collapse="|")
d_RRTitems <- d_RRTitems0 %>% filter(!str_detect(label, z))
d_RRTitems %>% head()
```

```{r base dialysis 1}
###Collect dialysis data.
###check dialysis from -7d to 1st_ABX
###With hadm to 1st_ABX time frame assessment, those are defined as KDIGO3 at 1st_ABX and excluded from primary outcome analysis. 

dial_chartevents <- ricu::load_src(ricu::mimic$chartevents, itemid %in% d_RRTitems$item) %>% dplyr::select(hadm_id, icustay_id, charttime, itemid) 
dial_output <- ricu::load_src(ricu::mimic$outputevents, itemid %in% d_RRTitems$item) %>% dplyr::select(hadm_id, icustay_id, charttime, itemid) 
dial_data <- rbind(dial_chartevents, dial_output) %>% subset(hadm_id %in% carbapenem_d$hadm_id) %>% 
              left_join(d_RRTitems, by=c("itemid"="item")) %>% distinct()
dial_data_b <- dial_data %>% left_join(carbapenem_d %>% dplyr::select(hadm_id, hadm_first_carbapenem_start, time_switch_group), by="hadm_id")
dial_data_b$time_dial_to_1stabx <- difftime(dial_data_b$charttime, dial_data_b$hadm_first_carbapenem_start, units = "hours")

dial_data_1st <- dial_data_b %>% subset(time_dial_to_1stabx>-168.1&time_dial_to_1stabx<168.1&time_dial_to_1stabx<time_switch_group) %>% group_by(hadm_id) %>% filter(time_dial_to_1stabx==min(time_dial_to_1stabx)) #delete daila after group switch
```

**\_\_**

##### **Add age, sex, sofa score and base AKI stage to a master dataframe**

```{r Put base_KDIGO factors to carbapenem_DF}
#Add age, sex, icd9, sofa, base AKI data to master DF
carbapenem_e <- carbapenem_d %>% left_join(age, by="icustay_id") %>% left_join(sex, by="icustay_id") %>% left_join(bmi, by="icustay_id") %>% 
  left_join(icd9_df, by="icustay_id") %>% 
  left_join(sofa3 %>% dplyr::select(icustay_id, sofa), by="icustay_id") %>% 
  left_join(sofa_cns3 %>% dplyr::select(icustay_id, sofa_cns), by="icustay_id") %>% 
  left_join(sofa_renal3 %>% dplyr::select(icustay_id, sofa_renal), by="icustay_id") %>% 
  left_join(sep3 %>% dplyr::select(icustay_id, sep3), by="icustay_id") %>% 
  left_join(qsofa3 %>% dplyr::select(icustay_id, qsofa), by="icustay_id") %>% 
  left_join(sirs3 %>% dplyr::select(icustay_id, sirs), by="icustay_id") %>% 
  left_join(bef_creatinine_c %>% dplyr::select(hadm_id, base_creatinine, near_crea, KDIGO_crea), by="hadm_id") %>% 
  left_join(dial_data_1st %>% dplyr::select(hadm_id, time_dial_to_1stabx), by="hadm_id") %>% distinct()

carbapenem_e <- carbapenem_e %>% rename("base_KDIGO_crea"=KDIGO_crea)
carbapenem_e$base_KDIGO_dial <- ifelse(is.na(carbapenem_e$time_dial_to_1stabx),0, ifelse(carbapenem_e$time_dial_to_1stabx<0, 3, 0))
carbapenem_e$base_KDIGO <- pmax(carbapenem_e$base_KDIGO_crea, carbapenem_e$base_KDIGO_dial)
carbapenem_e$sofa_cns <- ifelse(is.na(carbapenem_e$sofa_cns), 0, carbapenem_e$sofa_cns) #30-40 sofa_cns are NA probably due to sedation (no NA for sofa_renal). inpute 0
carbapenem_e$sofa_others0 <- carbapenem_e$sofa - carbapenem_e$sofa_cns - carbapenem_e$sofa_renal
carbapenem_e$sofa_others <- ifelse(carbapenem_e$sofa_others0<0, 0, carbapenem_e$sofa_others0)
#carbapenem_e %>% dplyr::select(sofa, sofa_cns, sofa_renal, sofa_others) %>% summary()
```

\_\_

\_\_

#### [**Next, outcome assessment.**]{.underline}

#### **8. Collect data for outcome assessment (AKI until day 7 after initiation of carbapenems)**

##### **First, use creatinine data for outcome assessment.**

```{r outcome creatinine, message=F}
###Put creatinine values after treatment and until 7d after treatment
ICU_creatinine <- creatinine_c %>% subset(time_abx_to_Crea >-0.1 & time_abx_to_Crea <168.1& time_abx_to_Crea<time_switch_group) %>% dplyr::select(creatinine, hadm_id, icustay_id, time_ICUadmit_to_abx, time_abx_to_Crea, base_creatinine, near_crea)



###Assess KDIGO changes with creatinine increase after treatment.
###Assess the ratio of each measured creatinine to base creatinine, converting to KDIGO
ICU_creatinine$ratio_to_base <- ICU_creatinine$creatinine/ICU_creatinine$base_crea
ICU_creatinine$KDIGO_ratio <- ifelse(ICU_creatinine$base_crea>4, 3,
                                  ifelse(ICU_creatinine$creatinine>4, 3,
                                   ifelse(ICU_creatinine$ratio_to_base>3, 3,
                                    ifelse(ICU_creatinine$ratio_to_base>2, 2,
                                     ifelse(ICU_creatinine$ratio_to_base>1.5, 1 ,0)))))

###Assess creatinine increase>0.3 within 48h
ICU_creatinine$diff_to_base <- ICU_creatinine$creatinine - ICU_creatinine$base_crea
ICU_creatinine$KDIGO_dif48 <- ifelse(ICU_creatinine$diff_to_base<0.3, 0, ifelse(ICU_creatinine$time_abx_to_Crea<48, 1, 0))

ICU_creatinine$KDIGO_crea <- pmax(ICU_creatinine$KDIGO_ratio, ICU_creatinine$KDIGO_dif48)
  
  
###calculate max crea ratio/diff for secondary outcoes assessment
ICU_creatinine_summary <- ICU_creatinine %>% group_by(hadm_id) %>% 
                          summarize("outcome_KDIGO_crea"=max(KDIGO_crea),
                                    "outcome_max_crea_ratio"=max(ratio_to_base), 
                                    "outcome_max_crea_diff"=max(diff_to_base))

###Collect dialysis event. get outcome. Get first HD in the icustay
ICU_dialevents_1st_summary <- dial_data_1st %>% subset(time_dial_to_1stabx>0) %>% summarize(time_dial_to_1stabx=min(time_dial_to_1stabx)) %>% mutate("outcome_KDIGO_dial"=3)

###add to master DF
carbapenem_f <- carbapenem_e %>% left_join(ICU_creatinine_summary, by="hadm_id") %>% left_join(ICU_dialevents_1st_summary, dplyr::select(hadm_id, time_dial_to_1stabx, outcome_KDIGO_dial), by="hadm_id") %>% distinct()
carbapenem_f$outcome_KDIGO_dial <- ifelse(is.na(carbapenem_f$outcome_KDIGO_dial), 0, 3)
carbapenem_f$outcome_KDIGO <- pmax(carbapenem_f$outcome_KDIGO_dial, carbapenem_f$outcome_KDIGO_crea)
carbapenem_f$outcome_KDIGO_inc <- ifelse(carbapenem_f$base_KDIGO==3, NA, 
                                    ifelse(carbapenem_f$base_KDIGO<carbapenem_f$outcome_KDIGO, T, F))
carbapenem_f$outcome_new_dial <- ifelse(carbapenem_f$base_KDIGO_dial==3, NA, 
                                        ifelse(carbapenem_f$outcome_KDIGO_dial==3, T, F))
```

\_\_

#### **9. Other secondary outcomes**

##### LOS_ICU, LOS_hospital, death in hospital (since mean value is 240 hr, those would be death in hospital not in ICU). 

```{r Get dialysis outcome (between 1st Abx and ICU discharge, message=F}
#Get ohter outcome data using "load_concept"
ICU_intime_summary <- ricu::load_src(ricu::mimic$transfers) %>% filter(!is.na(icustay_id)) %>% group_by(icustay_id) %>% summarize("ICU_intime"=min(intime))
death_DF0 <- ricu::load_concepts("death", src="mimic") %>% 
                left_join(ICU_intime_summary, by="icustay_id") %>% mutate("time_death" = ICU_intime + index_var) %>% 
                left_join(carbapenem_e %>% dplyr::select(icustay_id, hadm_id, hadm_first_carbapenem_start, time_switch_group)) %>%
                filter(!is.na(hadm_first_carbapenem_start)) %>% mutate("time_abx_to_death" = time_death - hadm_first_carbapenem_start)
death_DF <- death_DF0 %>% filter(time_abx_to_death<168, time_abx_to_death<time_switch_group) #erase data after group switch

los_hosp_DF0 <- ricu::load_concepts("los_hosp", src="mimic") %>%
                left_join(ICU_intime_summary, by="icustay_id") %>% mutate("time_loshp" = ICU_intime + los_hosp*3600*24) %>% 
                left_join(carbapenem_e %>% dplyr::select(icustay_id, hadm_id, hadm_first_carbapenem_start, time_switch_group)) %>%
                filter(!is.na(hadm_first_carbapenem_start)) %>% mutate("time_abx_to_loshp" = time_loshp - hadm_first_carbapenem_start)
los_hosp_DF0$time_abx_to_loshp <- as.numeric(los_hosp_DF0$time_abx_to_loshp, units="hours")
los_hosp_DF <- los_hosp_DF0 %>% filter(time_abx_to_loshp<168, time_abx_to_loshp<time_switch_group) #erase data after group switch


dep_type_DF <- ricu::load_concepts("adm", src="mimic") %>% filter(icustay_id %in% carbapenem_f$icustay_id) %>% as.data.frame() %>% rename("dep_type" = adm)
ethnicity_DF <- ricu::mimic$admissions %>% as.data.frame() %>% filter(hadm_id %in% carbapenem_f$hadm_id) %>% dplyr::select(hadm_id, ethnicity)

#add to master DF
carbapenem_g <- carbapenem_f %>% left_join(., los_hosp_DF %>% dplyr::select(hadm_id, time_abx_to_loshp), by="hadm_id") %>% 
                                 left_join(., death_DF %>% dplyr::select(hadm_id, time_abx_to_death), by="hadm_id") %>% 
                                 left_join(., dep_type_DF, by="icustay_id") %>% 
                                 left_join(., ethnicity_DF, by="hadm_id") %>% distinct()

carbapenem_g$death_in_hosp <- ifelse(is.na(carbapenem_g$time_abx_to_death), F, T)
carbapenem_g$death_in_7d <- ifelse(is.na(carbapenem_g$time_abx_to_death), F, 
                                                 ifelse(carbapenem_g$time_abx_to_death <168, T, F))
carbapenem_g$outcome_KDIGO_inc_or_death <- ifelse(is.na(carbapenem_g$outcome_KDIGO_inc), NA, 
                                            ifelse(carbapenem_g$outcome_KDIGO_inc==T, T,
                                             ifelse(carbapenem_g$death_in_7d==T,T, F)))
carbapenem_g$base_crea <- carbapenem_g$base_creatinine
```

```{r r3 culture, message=F}
#cult_names <- "culture|CULTURE|Culture"
cult_names <- "BLOOD CULTURE"
non_cult_names <- "viral|VIRAL|Viral"

m3_cult<- ricu::mimic$microbiologyevents[grep(cult_names, ricu::mimic$microbiologyevents$spec_type_desc, ignore.case=TRUE),] %>% .[!grep(non_cult_names, .$spec_type_sesc)] %>% dplyr::select(hadm_id, charttime) %>% left_join(carbapenem_g %>% dplyr::select(hadm_id, hadm_first_carbapenem_start), by="hadm_id") %>% filter(!is.na(hadm_first_carbapenem_start)) %>% mutate("time_cult_to_1stabx"=(charttime-hadm_first_carbapenem_start) %>% as.numeric()/3600) %>% filter(time_cult_to_1stabx> -72 & time_cult_to_1stabx<24) %>% mutate("pre_blood_culture"=T) %>% distinct()

carbapenem_h <- carbapenem_g %>% left_join(m3_cult %>% dplyr::select(hadm_id, pre_blood_culture)) %>% distinct()
carbapenem_h$pre_blood_culture <- ifelse(is.na(carbapenem_h$pre_blood_culture), F,
                                              ifelse(carbapenem_h$pre_blood_culture==F, F, T))
```

```{r vancomycin}
van_names <- "vanco|firvanq|lyphocin"
received_van <- ricu::mimic$prescriptions[grep(van_names, ricu::mimic$prescriptions$drug, ignore.case=TRUE),]
received_van$starttime <- received_van$startdate + dminutes(780)
received_van$drug %>% unique()

received_van2 <- left_join(received_van %>% dplyr::select(hadm_id, starttime),
                              carbapenem_h %>% dplyr::select(hadm_id, hadm_first_carbapenem_start), by="hadm_id") %>% na.omit() %>% 
  mutate("hour_van_to_abx"=(starttime-hadm_first_carbapenem_start)/3600 %>% as.numeric()) %>% filter(abs(hour_van_to_abx)<24) %>% mutate("treat_van"=T)

carbapenem_i <- left_join(carbapenem_h, received_van2 %>% dplyr::select(hadm_id, treat_van), by="hadm_id") %>% distinct() %>% mutate("treat_van"=ifelse(is.na(treat_van), F, T))
```

```{r vaso, message=F}
vaso <-
rbind(
ricu::load_concepts("adh_rate", src="mimic") %>% filter(icustay_id %in% carbapenem_i$icustay_id) %>% .[,1:2],
ricu::load_concepts("dobu_rate", src="mimic") %>% filter(icustay_id %in% carbapenem_i$icustay_id) %>% .[,1:2],
ricu::load_concepts("dopa_rate", src="mimic") %>% filter(icustay_id %in% carbapenem_i$icustay_id) %>% .[,1:2],
ricu::load_concepts("epi_rate", src="mimic") %>% filter(icustay_id %in% carbapenem_i$icustay_id) %>% .[,1:2],
ricu::load_concepts("norepi_rate", src="mimic") %>% filter(icustay_id %in% carbapenem_i$icustay_id) %>% .[,1:2],
ricu::load_concepts("phn_rate", src="mimic") %>% filter(icustay_id %in% carbapenem_i$icustay_id) %>% .[,1:2]) 


vaso2 <- vaso %>% left_join(ICU_intime_summary, by="icustay_id") %>% mutate("vaso_time"=charttime+ICU_intime)
vaso3 <- vaso2 %>% left_join(carbapenem_i %>% dplyr::select(icustay_id, hadm_first_carbapenem_start), by="icustay_id") %>% mutate("time_abx_to_vaso"=(vaso_time-hadm_first_carbapenem_start)) 

vaso3$time_abx_to_vaso <- as.numeric(vaso3$time_abx_to_vaso, units="hours")
vaso4 <- vaso3 %>% filter(time_abx_to_vaso> -168 & time_abx_to_vaso<0) %>% group_by(hadm_id) %>% summarize("vasopressor"=min(time_abx_to_vaso))

carbapenem_j <- carbapenem_i %>% left_join(vaso4) %>% distinct()
carbapenem_j$vasopressor <- ifelse(is.na(carbapenem_j$vasopressor), F, T)
```

```{r vent, message=F}
vent <- rbind(
ricu::load_concepts("vent_ind", src="mimic") %>% filter(icustay_id %in% carbapenem_j$icustay_id) %>% .[,1:3],
ricu::load_concepts("mech_vent", src="mimic") %>% filter(icustay_id %in% carbapenem_j$icustay_id) %>% .[,1:3]) 
  
vent2 <- vent %>% left_join(ICU_intime_summary, by="icustay_id") %>% 
                  left_join(carbapenem_j %>% dplyr::select(hadm_id, icustay_id, hadm_first_carbapenem_start), by="icustay_id") %>% 
                  mutate("time_abx_to_vent_start"=as.numeric(starttime+ICU_intime-hadm_first_carbapenem_start, unit="hours"),
                         "time_abx_to_vent_end"=vent_dur+time_abx_to_vent_start) %>% 
                  filter((time_abx_to_vent_start<0 & time_abx_to_vent_end>0)) %>% mutate(ventilation=T) %>% distinct()

carbapenem_k <- carbapenem_j %>% left_join(vent2 %>% dplyr::select(hadm_id, icustay_id, ventilation), by="hadm_id") %>% distinct()
carbapenem_k$ventilation <- ifelse(is.na(carbapenem_k$ventilation), F, T)
```

```{r carbapenems count, message=F}
carbapenems$drug2 <- ifelse(carbapenems$drug=="Imipenem-Cilastatin *NF*", "Imipenem-Cilastatin",
                            ifelse(carbapenems$drug=="*NF* Ertapenem Sodium", "Ertapenem",
                                   ifelse(carbapenems$drug=="Doripenem *NF*", "Doripenem", carbapenems$drug)))

carbapenems_counts <- 
carbapenems %>% filter(drug!="Meropenem Desensitization") %>% dplyr::select(hadm_id, drug2, startdate2) %>% 
  left_join(carbapenem_k %>% dplyr::select(hadm_id, hadm_first_carbapenem_start), by="hadm_id") %>% 
  mutate("time_first_abx_to_abx"=difftime(startdate2, hadm_first_carbapenem_start)/3600) %>% filter(time_first_abx_to_abx<168) %>% 
  group_by(hadm_id, drug2) %>% summarise(n()) %>% pivot_wider(names_from = drug2, values_from = "n()") %>% mutate("Imipenem/Cilastatin/Relebactam"=0)

carbapenems_counts[is.na(carbapenems_counts)] <- 0

carbapenem_l <- left_join(carbapenem_k, carbapenems_counts, by="hadm_id")
```

```{r observation period, message=F}
crea_ob_DF <- creatinine %>% rename("crea_time" = charttime) %>% left_join(carbapenem_l, by="hadm_id") %>% distinct() %>% 
              mutate("time_abx_to_crea"=difftime(crea_time, hadm_first_carbapenem_start, units = "hours")) %>% 
              group_by(hadm_id) %>% summarize('last_crea'=max(time_abx_to_crea)) %>% na.omit()
dial_ob_DF <- dial_data_b %>% group_by(hadm_id) %>% summarize('last_dial'=max(time_dial_to_1stabx)) 

obs_summary <- crea_ob_DF %>% dplyr::select(hadm_id, last_crea) %>% 
                left_join(dial_ob_DF %>% dplyr::select(hadm_id, last_dial), by="hadm_id") %>% 
                left_join(death_DF0 %>% dplyr::select(hadm_id, time_abx_to_death), by="hadm_id") %>% 
                left_join(los_hosp_DF0 %>% dplyr::select(hadm_id, time_abx_to_loshp), by="hadm_id") %>% 
               left_join(carbapenem_l %>% dplyr::select(hadm_id, time_switch_group), by="hadm_id")

obs_summary$obs_period0 <- pmax(obs_summary$last_crea, obs_summary$last_dial, obs_summary$time_abx_to_death, obs_summary$time_abx_to_loshp, na.rm = T)
obs_summary$obs_period <- pmin(obs_summary$obs_period0, obs_summary$time_switch_group, 168, na.rm = T)
carbapenem_m <- left_join(carbapenem_l, obs_summary %>% dplyr::select(hadm_id, obs_period, time_abx_to_death, time_abx_to_loshp), by="hadm_id")
```

```{r data save}
saveRDS(creatinine_c, "creatinine_c.rds")
write.csv(carbapenem_m, "MDF_mimic3.csv")
read.csv("MDF_mimic3.csv")  %>% group_by(drug_type) %>% summarise(n()) %>% 
  cbind(read.csv("MDF_mimic3.csv") %>% filter(base_KDIGO<2.9) %>% group_by(drug_type) %>% summarise(n()) %>% dplyr::select(-drug_type))
```